### 2023-03-01 paper/main.tex
new repository

\documentclass{article}
\usepackage{arxiv}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algpseudocode}

\newtheorem*{assumption*}{\assumptionnumber}
\providecommand{\assumptionnumber}{}
\makeatletter
\newenvironment{assumption}[2]
 {%
  \renewcommand{\assumptionnumber}{\textbf{Assumption} #1 ({#2})}%
  \begin{assumption*}%
  \protected@edef\@currentlabel{#1-#2}%
 }
 {%
  \end{assumption*}
 }

\title{A template for the \emph{arxiv} style}

\author{ Kreinin M. \\
	Department of Intelligent Systems\\
	MIPT\\
	Moscow, Russia \\
	\texttt{kreinin.mv@phystech.edu} \\
}
\date{}

\renewcommand{\shorttitle}{\textit{arXiv} Template}

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
pdftitle={A template for the arxiv style},
pdfsubject={q-bio.NC, q-bio.QM},
pdfauthor={Kreinin M.},
pdfkeywords={First keyword, Second keyword, More},
}

\begin{document}
\maketitle

\begin{abstract}
	This paper examines the convergence rate of adaptive gradient methods when a regularization function is added to the target function. This is an area of research, since many machine learning problems use the heuristic, heuristic regularization, and we investigate the theoretical and practical convergence of adaptive gradient methods.

	% В данной статье рассматривается скорость сходимости адаптивных градиентных методов при добавлении к целевой функции функцию регуляризации. Эта область требует исследования, т.к. при решении многих задач машинного обучения используется эвристика - эвристрегуляризация, и мы исследуем теоретически и практически  сходимость адаптивных градиентных методов.
\end{abstract}

\keywords{Adam \and OASIS \and Regularization \and ADAHessian}

\section{Introduction}
We consider the unconstrained optimization problem
\begin{equation*}
	\min_{w \in \mathbb{R}^d} f(w)
\end{equation*}
Problems of the form cover a plethora of applications, including empirical risk minimization,
deep learning, and supervised learning tasks such as regularized least squares or logistic regression.

But we can add regulirazation $r(w)$ -- regularization, and solve the unconstrained optimization problem.
\begin{equation*}
	\min_{w \in \mathbb{R}^d} F(w) = f(w) + r(w)
\end{equation*}

For solving these problems we always scaled adaptive gradients algorithms like ADAM, OASIS, ADAHessian. We investigate how the convergence rate will change when the regularization function is added to these algorithms.
\if 0
\begin{algorithm}[H]
	\caption{Based algorithm}\label{alg:Based}
	$w_0, D_0, \eta_0$
	\begin{algorithmic}
		\For{$k = 1, 2, ...$}
		\State $D_k$ - update
		\State $\eta_k$ - update
		\State Set $w_{k+1} = w_k - \eta_k D_k^{-1} \nabla F(w_k)$
		\EndFor
	\end{algorithmic}
\end{algorithm}
\fi

\if 0
Examples of similars algorithms.
\begin{algorithm}[H]
	\caption{Adam}\label{alg:Adam}
		\begin{algorithmic}
		\Require{$\alpha, \beta_1, \beta_2, \epsilon, f$}
		\State $m_0 = 0$ -- 1-st moment vector
		\State $v_0 = 0$ -- 2-nd moment vector
		\State $t = 0$ -- timestep

		\While {$\theta$ not converged}
			\State $t = t+1$
			\State $g_t = \nabla_{\theta} f_t(\theta_{t-1})$
			\State $m_t = \beta_1 \cdot m_{t-1} + (1 - \beta_1) \cdot g_t$
			\State $v_t = \beta_2 \cdot v_{t-1} + (1 - \beta_2) \cdot g_t^2$
			\State $\hat{m_t} = \frac{m_t}{1-\beta_1^t}$
			\State $\hat{v_t} = \frac{v_t}{1-\beta_2^t}$
			\State $\theta_t = \theta_{t-1} - \alpha \cdot \frac{\hat{m_t}}{\sqrt{v_t} + \epsilon}$
		\EndWhile
	\end{algorithmic}
	\end{algorithm}

	\begin{algorithm}[H]
	\caption{OASIS}\label{alg:OASIS}
	\begin{algorithmic}
		\Require{$w_0, \eta_0, D_0, \theta_0 = + \infty$}    
		\State $w_1 = w_0 - \eta \hat{D_0}^{-1} \nabla F(w_0)$

		\For{$k = 1, 2, ...$}
		\State $D_k = \beta D_{k-1} + (1-\beta_2) \cdot diag\left( z_k \odot \nabla^2 F(w_k) z_k \right)$
		\State $(\hat{D_k})_{ii} = max \{|D_k|_{i, i} ; \alpha \}$, $\forall i = \overline{1, d}$
		\State $\eta_k = min \{ \sqrt{1 + \theta_{k-1}} \cdot \eta_{k-1}; \frac{||w_k - w_{k-1}||_{\hat{D_k}}}{2 ||\nabla F(w_k) - \nabla F(w_{k-1}) ||_{\hat{D_k}}^* } \}$
		\State $\theta_k = \frac{\eta_k}{\eta_{k-1}}$
		\EndFor

	\end{algorithmic}
\end{algorithm}
\fi

% В исследуемом нами алгоритме сходимости мы будем исследовать алгоритмы двух следующих видов. В первом функция регуляризации выносится отдельном в пересчете весов модели, во втором функция домножается на обратный "гессиан".
In the convergence algorithm that we study, we will investigate algorithms of the following two kinds. In the first one, the regularization function is taken out separately in the recalculation of model weights, and in the second one, the function is dominated by the inverse "hessian".

\begin{algorithm}[H]
	\caption{Based algorithm}\label{alg:Based}
	$w_0, D_0, \eta_0$
	\begin{algorithmic}
		\For{$k = 1, 2, ...$}
		\State $D_k$ - update by using information of $f(w)$
		\State $\eta_k$ - update
		\State Set $w_{k+1} = w_k - \eta_k D_k^{-1} \nabla f(w_k) - \eta \nabla r(w)$ 
		\State or like that
		\State Set $w_{k+1} = w_k - \eta_k D_k^{-1} (\nabla f(w_k) + \nabla r(w))$
		\EndFor
	\end{algorithmic}
\end{algorithm}

Some assumptions for our problem: 
\begin{assumption}{1}{Convex}
	The function f is convex, i.e. $\forall w, w' \in \mathbb{R}^d$
	\begin{equation}
		f(w) \geq f(w') + \langle \nabla F(w'), w-w' \rangle
	\end{equation}
\end{assumption}

\begin{assumption}{2}{L-smoothness}
	The gradients of F are L-Lipschitz continuous $\forall w \in \mathbb{R}^d$, i.e. there exists a constant $L > 0$ such that $\forall w, w' \in \mathbb{R}^d$,
	\begin{equation*}
		f(w) \leq f(w') + \langle \nabla f(w'), w-w' \rangle + \frac{L}{2} ||w - w'||^2
	\end{equation*}
\end{assumption}

\begin{assumption}{3}{Twice differentiable}
	The function f is twice continuously differentiable.
\end{assumption}

\begin{assumption}{4}{$\mu$ - strongly convex}
	The function f is $\mu$-strongly convex, i.e., there exists a constant $\mu > 0$ such that $\forall w, w' \in \mathbb{R}^d$
	\begin{equation*}
		f(w) \geq f(w') + \langle f(w'), w-w' \rangle +\frac{\mu}{2} ||w - w'||^2
	\end{equation*}

\end{assumption}

%\section{Headings: first level}
%\label{sec:headings}
% See Section \ref{sec:headings}.
%\subsection{Headings: second level}
%\subsubsection{Headings: third level}
%\paragraph{Paragraph}
%\section{Examples of citations, figures, tables, references}
%\label{sec:others}

\subsection{Citations}

\cite{kingma2014adam}, \cite{jahani2021doubly}, \cite{sadiev2022stochastic}, \cite{beznosikov2022scaled}, \cite{stich2019unified}

%\subsection{Figures}
%See Figure \ref{fig:fig1}. Here is how you add footnotes. \footnote{Sample of the first footnote.}
%\begin{figure}
	%\centering
	%\includegraphics[width=0.5\textwidth]{../figures/log_reg_cs_exp.eps}
	%\caption{Sample figure caption.}
	%\label{fig:fig1}
%\end{figure}

%\subsection{Tables}
%See awesome Table~\ref{tab:table}.
%The documentation for \verb+booktabs+ (`Publication quality tables in LaTeX') is available from:
%\begin{center}
%	%\url{https://www.ctan.org/pkg/booktabs}
%\end{center}

\if 0
\begin{table}
	\caption{Sample table title}
	\centering
	\begin{tabular}{lll}
		\toprule
		\multicolumn{2}{c}{Part}                   \\
		\cmidrule(r){1-2}
		Name     & Description     & Size ($\mu$m) \\
		\midrule
		Dendrite & Input terminal  & $\sim$100     \\
		Axon     & Output terminal & $\sim$10      \\
		Soma     & Cell body       & up to $10^6$  \\
		\bottomrule
	\end{tabular}
	\label{tab:table}
\end{table}
\fi
\if 0
\subsection{Lists}
\begin{itemize}
	\item Lorem ipsum dolor sit amet
	\item consectetur adipiscing elit.
	\item Aliquam dignissim blandit est, in dictum tortor gravida eget. In ac rutrum magna.
\end{itemize}
\fi

\bibliographystyle{unsrtnat}
\bibliography{references}

\end{document}

### 2023-03-02 paper/main.tex
update abstract, introduction and problem statement

@@
 This is an area of research, since many machine learning problems use the heuristic, heuristic regularization, and we investigate the theoretical and practical convergence of adaptive gradient methods.
-
-	% В данной статье рассматривается скорость сходимости адаптивных градиентных методов при добавлении к целевой функции функцию регуляризации.
-Эта область требует исследования, т.к.
-при решении многих задач машинного обучения используется эвристика - эвристрегуляризация, и мы исследуем теоретически и практически  сходимость адаптивных градиентных методов.
 \end{abstract}
@@
 \section{Introduction}
+In machine learning we consider optimization problem
+\begin{equation*}
+	\min_{w \in \mathbb{R}^d} f(w)
+\end{equation*}
+Problems of the form (1) cover a plethora of applications, including empirical risk minimization,
+deep learning, and supervised learning tasks such as regularized least squares or logistic regression. This minimization problem can be difficult to solve, particularly when the number of training
+samples n, or problem dimension d, is large, or if the problem is nonconvex.
+
+There are second order preconditioners methods for solving this problem, such as Adam, OASIS, AdaHessian.
+
+Throughout this work we assume that each f $:\mathbb{R}^d \rightarrow \mathbb{R}$ is twice differentiable and also L-smooth. This is formalized in the following assumption.
+
+\begin{assumption}{1}{Convex}
+	The function f is convex, i.e. $\forall w, w' \in \mathbb{R}^d$
+	\begin{equation}
+		f(w) \geq f(w') + \langle \nabla F(w'), w-w' \rangle
+	\end{equation}
+\end{assumption}
+
+\begin{assumption}{2}{L-smoothness}
+	The gradients of F are L-Lipschitz continuous $\forall w \in \mathbb{R}^d$, i.e. there exists a constant $L > 0$ such that $\forall w, w' \in \mathbb{R}^d$,
+	\begin{equation*}
+		f(w) \leq f(w') + \langle \nabla f(w'), w-w' \rangle + \frac{L}{2} ||w - w'||^2
+	\end{equation*}
+\end{assumption}
+
+\begin{assumption}{3}{Twice differentiable}
+	The function f is twice continuously differentiable.
+\end{assumption}
+
+\begin{assumption}{4}{$\mu$ - strongly convex}
+	The function f is $\mu$-strongly convex, i.e., there exists a constant $\mu > 0$ such that $\forall w, w' \in \mathbb{R}^d$
+	\begin{equation*}
+		f(w) \geq f(w') + \langle f(w'), w-w' \rangle +\frac{\mu}{2} ||w - w'||^2
+	\end{equation*}
+
+\end{assumption}
+
+\section{Problem statement}
 We consider the unconstrained optimization problem
@@
 
-Some assumptions for our problem: 
-\begin{assumption}{1}{Convex}
-	The function f is convex, i.e. $\forall w, w' \in \mathbb{R}^d$
-	\begin{equation}
-		f(w) \geq f(w') + \langle \nabla F(w'), w-w' \rangle
-	\end{equation}
-\end{assumption}
-
-\begin{assumption}{2}{L-smoothness}
-	The gradients of F are L-Lipschitz continuous $\forall w \in \mathbb{R}^d$, i.e. there exists a constant $L > 0$ such that $\forall w, w' \in \mathbb{R}^d$,
-	\begin{equation*}
-		f(w) \leq f(w') + \langle \nabla f(w'), w-w' \rangle + \frac{L}{2} ||w - w'||^2
-	\end{equation*}
-\end{assumption}
-
-\begin{assumption}{3}{Twice differentiable}
-	The function f is twice continuously differentiable.
-\end{assumption}
-
-\begin{assumption}{4}{$\mu$ - strongly convex}
-	The function f is $\mu$-strongly convex, i.e., there exists a constant $\mu > 0$ such that $\forall w, w' \in \mathbb{R}^d$
-	\begin{equation*}
-		f(w) \geq f(w') + \langle f(w'), w-w' \rangle +\frac{\mu}{2} ||w - w'||^2
-	\end{equation*}
-
-\end{assumption}
-
 %\section{Headings: first level}

### 2023-03-06 code/main.py
add simple baseline for experementing with neuralnetworks

@@ -1,0 +1,161 @@
+'''Train CIFAR10 with PyTorch.'''
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import torch.nn.functional as F
+import torch.backends.cudnn as cudnn
+
+import torchvision
+import torchvision.transforms as transforms
+
+import os
+import argparse
+
+from models import *
+from tqdm import tqdm
+#from torch.utils import progress_bar
+from torch.utils.tensorboard import SummaryWriter
+
+if __name__ == '__main__': # protect your program's entry point
+    
+
+    parser = argparse.ArgumentParser(description='PyTorch CIFAR10 Training')
+    parser.add_argument('--lr', default=0.1, type=float, help='learning rate')
+    parser.add_argument('--resume', '-r', action='store_true',
+                        help='resume from checkpoint')
+    args = parser.parse_args()
+    
+    device = 'cuda' if torch.cuda.is_available() else 'cpu'
+    best_acc = 0  # best test accuracy
+    start_epoch = 0  # start from epoch 0 or last checkpoint epoch
+    
+    # Data
+    print('==> Preparing data..')
+    transform_train = transforms.Compose([
+        transforms.RandomCrop(32, padding=4),
+        transforms.RandomHorizontalFlip(),
+        transforms.ToTensor(),
+        transforms.Normalize((0.4914, 0.4822, 0.4465), (0.2023, 0.1994, 0.2010)),
+    ])
+    
+    transform_test = transforms.Compose([
+        transforms.ToTensor(),
+        transforms.Normalize((0.4914, 0.4822, 0.4465), (0.2023, 0.1994, 0.2010)),
+    ])
+    
+    trainset = torchvision.datasets.CIFAR10(
+        root='./data', train=True, download=True, transform=transform_train)
+    trainloader = torch.utils.data.DataLoader(
+        trainset, batch_size=128, shuffle=True, num_workers=2)
+    
+    testset = torchvision.datasets.CIFAR10(
+        root='./data', train=False, download=True, transform=transform_test)
+    testloader = torch.utils.data.DataLoader(
+        testset, batch_size=100, shuffle=False, num_workers=2)
+    
+    classes = ('plane', 'car', 'bird', 'cat', 'deer',
+               'dog', 'frog', 'horse', 'ship', 'truck')
+    
+    # Model
+    print('==> Building model..')
+    # net = VGG('VGG19')
+    # net = ResNet18()
+    # net = PreActResNet18()
+    # net = GoogLeNet()
+    # net = DenseNet121()
[…]

### 2023-03-06 code/main.py
update main.py

@@ -59,7 +59,7 @@ if __name__ == '__main__': # protect your program's entry point
     # Model
     print('==> Building model..')
     # net = VGG('VGG19')
-    # net = ResNet18()
+    net = ResNet18()
     # net = PreActResNet18()
     # net = GoogLeNet()
     # net = DenseNet121()
@@ -72,8 +72,8 @@ if __name__ == '__main__': # protect your program's entry point
     # net = ShuffleNetV2(1)
     # net = EfficientNetB0()
     # net = RegNetX_200MF()
-    net = SimpleDLA()
-    writer = SummaryWriter('SimpleDla')
+    #net = SimpleDLA()
+    #writer = SummaryWriter('SimpleDla')
     net = net.to(device)
     if device == 'cuda':
         net = torch.nn.DataParallel(net)
@@ -89,10 +89,10 @@ if __name__ == '__main__': # protect your program's entry point
         start_epoch = checkpoint['epoch']
     
     criterion = nn.CrossEntropyLoss()
-    optimizer = optim.SGD(net.parameters(), lr=1e-2,
-                          momentum=0.9, weight_decay=5e-4)
+    #optimizer = optim.SGD(net.parameters(), lr=args.lr, momentum=0.9, weight_decay=5e-4)
+    optimizer = optim.AdamW(net.parameters(), lr=0.01, betas = (0.9, 0.999), eps=1e-8, weight_decay=2*1e-2)
     scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optimizer, T_max=200)
-    num_epoch = 200
+    num_epoch = 50
     
     # Training
     def train(epoch):
@@ -154,7 +154,7 @@ if __name__ == '__main__': # protect your program's entry point
             best_acc = acc
     
     
-    for epoch in range(start_epoch, start_epoch+200):
+    for epoch in range(start_epoch, start_epoch+num_epoch):
         train(epoch)
         test(epoch)
         scheduler.step()

### 2023-03-08 paper/main.tex
update title
add experiment

@@
 
-\title{A template for the \emph{arxiv} style}
+\title{Methods with preconditioning with weight decay regularization}
 
@@
 	\texttt{kreinin.mv@phystech.edu} \\
+	\And
+	Beznosikov A. \\
+	Department of Data Science\\
+	MIPT\\
+	Dolgoprudny, Russia \\
+	\texttt{beznosikov.an@phystech.edu} \\
 }
@@
 
-\keywords{Adam \and OASIS \and Regularization \and ADAHessian}
+\keywords{Adam \and OASIS \and Regularization \and ADAHessian \and Weight Decay}
 
@@
 We investigate how the convergence rate will change when the regularization function is added to these algorithms.
-\if 0
-\begin{algorithm}[H]
-	\caption{Based algorithm}\label{alg:Based}
-	$w_0, D_0, \eta_0$
-	\begin{algorithmic}
-		\For{$k = 1, 2, ...$}
-		\State $D_k$ - update
-		\State $\eta_k$ - update
-		\State Set $w_{k+1} = w_k - \eta_k D_k^{-1} \nabla F(w_k)$
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-\fi
-
-\if 0
-Examples of similars algorithms.
-\begin{algorithm}[H]
-	\caption{Adam}\label{alg:Adam}
-		\begin{algorithmic}
-		\Require{$\alpha, \beta_1, \beta_2, \epsilon, f$}
-		\State $m_0 = 0$ -- 1-st moment vector
-		\State $v_0 = 0$ -- 2-nd moment vector
-		\State $t = 0$ -- timestep
-
-		\While {$\theta$ not converged}
-			\State $t = t+1$
-			\State $g_t = \nabla_{\theta} f_t(\theta_{t-1})$
-			\State $m_t = \beta_1 \cdot m_{t-1} + (1 - \beta_1) \cdot g_t$
-			\State $v_t = \beta_2 \cdot v_{t-1} + (1 - \beta_2) \cdot g_t^2$
-			\State $\hat{m_t} = \frac{m_t}{1-\beta_1^t}$
-			\State $\hat{v_t} = \frac{v_t}{1-\beta_2^t}$
-			\State $\theta_t = \theta_{t-1} - \alpha \cdot \frac{\hat{m_t}}{\sqrt{v_t} + \epsilon}$
-		\EndWhile
-	\end{algorithmic}
-	\end{algorithm}
-
-	\begin{algorithm}[H]
-	\caption{OASIS}\label{alg:OASIS}
-	\begin{algorithmic}
-		\Require{$w_0, \eta_0, D_0, \theta_0 = + \infty$}    
-		\State $w_1 = w_0 - \eta \hat{D_0}^{-1} \nabla F(w_0)$
-
-		\For{$k = 1, 2, ...$}
-		\State $D_k = \beta D_{k-1} + (1-\beta_2) \cdot diag\left( z_k \odot \nabla^2 F(w_k) z_k \right)$
-		\State $(\hat{D_k})_{ii} = max \{|D_k|_{i, i} ; \alpha \}$, $\forall i = \overline{1, d}$
-		\State $\eta_k = min \{ \sqrt{1 + \theta_{k-1}} \cdot \eta_{k-1}; \frac{||w_k - w_{k-1}||_{\hat{D_k}}}{2 ||\nabla F(w_k) - \nabla F(w_{k-1}) ||_{\hat{D_k}}^* } \}$
-		\State $\theta_k = \frac{\eta_k}{\eta_{k-1}}$
-		\EndFor
-
-	\end{algorithmic}
-\end{algorithm}
-\fi
 
@@
 
-%\section{Headings: first level}
-%\label{sec:headings}
-% See Section \ref{sec:headings}.
-%\subsection{Headings: second level}
-%\subsubsection{Headings: third level}
-%\paragraph{Paragraph}
-%\section{Examples of citations, figures, tables, references}
-%\label{sec:others}
+\section{Experiment}
+% Мы проведем эксперимент, в котором сравним Adam с добавленной L2 регуляризацией с AdamW, при различных learning rate и decoupled weight, также мы сравним его с измененным алгоритмом AdamW, где регуляризатор занесен под гессиан, также мы сравним его при условии, что теперь минимальное собственное число гессиана, это не epsilon, а гиперпараметр decoupled weight.Проведем те же эксперименты со SGD и L2 регуляризацией и SGD с decoupled weitght при тех же параметрах.
+Все эксперименты будут проводиться на батчах размера 128, на сетке ResNet18, в 200 эпох.
+Всё это будет реализовано с помощью библиотеки PyTorch на dataset CIFAR10.
 
-\subsection{Citations}
-
-\cite{kingma2014adam}, \cite{jahani2021doubly}, \cite{sadiev2022stochastic}, \cite{beznosikov2022scaled}, \cite{stich2019unified}
-
-%\subsection{Figures}
-%See Figure \ref{fig:fig1}. Here is how you add footnotes. \footnote{Sample of the first footnote.}
-%\begin{figure}
-	%\centering
-	%\includegraphics[width=0.5\textwidth]{../figures/log_reg_cs_exp.eps}
-	%\caption{Sample figure caption.}
-	%\label{fig:fig1}
-%\end{figure}
-
-%\subsection{Tables}
-%See awesome Table~\ref{tab:table}.
-%The documentation for \verb+booktabs+ (`Publication quality tables in LaTeX') is available from:
-%\begin{center}
-%	%\url{https://www.ctan.org/pkg/booktabs}
-%\end{center}
-
-\if 0
-\begin{table}
-	\caption{Sample table title}
-	\centering
-	\begin{tabular}{lll}
-		\toprule
-		\multicolumn{2}{c}{Part}                   \\
-		\cmidrule(r){1-2}
-		Name     & Description     & Size ($\mu$m) \\
-		\midrule
-		Dendrite & Input terminal  & $\sim$100     \\
-		Axon     & Output terminal & $\sim$10      \\
-		Soma     & Cell body       & up to $10^6$  \\
-		\bottomrule
-	\end{tabular}
-	\label{tab:table}
-\end{table}
-\fi
-\if 0
-\subsection{Lists}
-\begin{itemize}
-	\item Lorem ipsum dolor sit amet
-	\item consectetur adipiscing elit.
-	\item Aliquam dignissim blandit est, in dictum tortor gravida eget. In ac rutrum magna.
-\end{itemize}
-\fi
+We will conduct an experiment in which we compare Adam with added L2 regularization with AdamW, at different learning rate and decoupled weight, also we will compare it with the modified AdamW algorithm where the regularizer is put under the hessian, also we will compare it under the condition that now the minimal eigenvalue of hessian is not epsilon, but decoupled weight hyperparameter.We will conduct the same experiments with SGD and L2 regularization and SGD with decoupled weitght at the same parameters.
+All experiments will be performed on batches of size 128, on a ResNet18 grid of 200 epochs.
+All this will be implemented using the PyTorch library on dataset CIFAR10.
 

### 2023-03-08 code/main.py

@@ -90,7 +90,8 @@ if __name__ == '__main__': # protect your program's entry point
     
     criterion = nn.CrossEntropyLoss()
     #optimizer = optim.SGD(net.parameters(), lr=args.lr, momentum=0.9, weight_decay=5e-4)
-    optimizer = optim.AdamW(net.parameters(), lr=0.01, betas = (0.9, 0.999), eps=1e-8, weight_decay=2*1e-2)
+    optimizer = optim.new_AdamW(net.parameters(), lr=0.01, betas = (0.9, 0.999), eps=1e-8, weight_decay=2*1e-2)
+    #optimizer = optim.AdamW(net.parameters(), lr=0.01, betas = (0.9, 0.999), eps=1e-8, weight_decay=2*1e-2)
     scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optimizer, T_max=200)
     num_epoch = 50
     

### 2023-03-08 code/main.py
add prepared for experiments

@@ -10,14 +10,88 @@ import torchvision.transforms as transforms
 
 import os
 import argparse
+import sys
+
+from myadam import MyAdamW
 
 from models import *
 from tqdm import tqdm
 #from torch.utils import progress_bar
 from torch.utils.tensorboard import SummaryWriter
 
-if __name__ == '__main__': # protect your program's entry point
+
+def test(epoch):
+    global best_acc
+    global test_step
+    net.eval()
+    test_loss = 0
+    correct = 0
+    total = 0
+    with torch.no_grad():
+        loop = tqdm(enumerate(testloader), total=len(testloader), leave=False)
+        for batch_idx, (inputs, targets) in loop:
+            test_step += 1
+            inputs, targets = inputs.to(device), targets.to(device)
+            outputs = net(inputs)
+            loss = criterion(outputs, targets)
+
+            test_loss += loss.item()
+            _, predicted = outputs.max(1)
+            total += targets.size(0)
+            correct += predicted.eq(targets).sum().item()
+            
+            writer.add_scalar('Testing loss', test_loss/(batch_idx+1),global_step=test_step)
+            writer.add_scalar('Testing accuracy', 100.*correct/total, global_step=test_step)
+            
+            loop.set_description(f"{full_name}Epoch (Test)[{epoch}/{num_epoch}]")
+            loop.set_postfix(loss= test_loss/(batch_idx+1), acc=100.*correct/total,correct=correct, total=total)
+
+    # Save checkpoint.
+    acc = 100.*correct/total
+    if acc > best_acc:
+        print('Saving..')
+        state = {
+            'net': net.state_dict(),
+            'acc': acc,
+            'epoch': epoch,
+        }
+        if not os.path.isdir('checkpoint'):
+            os.mkdir('checkpoint')
+        torch.save(state, f'./checkpoint/ckpt{full_name}.pth')
+        best_acc = acc
+
+# Training
+def train(epoch):
+    #print('\nEpoch: %d' % epoch)
+    global train_step
+    net.train()
+    train_loss = 0
+    correct = 0
+    total = 0
+    loop = tqdm(enumerate(trainloader), total=len(trainloader), leave=False)
     
+    for batch_idx, (inputs, targets) in loop:
+        inputs, targets = inputs.to(device), targets.to(device)
+        optimizer.zero_grad()
+        outputs = net(inputs)
+        loss = criterion(outputs, targets)
+        loss.backward()
[…]

### 2023-03-08 code/myadam.py

@@ -1,0 +1,328 @@
+from torch.optim import AdamW
+import math
+import torch
+from torch import Tensor
+from typing import List
+
+class MyAdamW(AdamW):
+    @torch.no_grad()
+    def step(self, closure=None):
+        """Performs a single optimization step.
+
+        Args:
+            closure (Callable, optional): A closure that reevaluates the model
+                and returns the loss.
+        """
+        self._cuda_graph_capture_health_check()
+
+        loss = None
+        if closure is not None:
+            with torch.enable_grad():
+                loss = closure()
+
+        for group in self.param_groups:
+            params_with_grad = []
+            grads = []
+            exp_avgs = []
+            exp_avg_sqs = []
+            max_exp_avg_sqs = []
+            state_steps = []
+            amsgrad = group['amsgrad']
+            beta1, beta2 = group['betas']
+
+            for p in group['params']:
+                if p.grad is None:
+                    continue
+                params_with_grad.append(p)
+                if p.grad.is_sparse:
+                    raise RuntimeError('AdamW does not support sparse gradients')
+                grads.append(p.grad)
+
+                state = self.state[p]
+
+                # State initialization
+                if len(state) == 0:
+                    state['step'] = torch.zeros((1,), dtype=torch.float, device=p.device) \
+                        if self.defaults['capturable'] else torch.tensor(0.)
+                    # Exponential moving average of gradient values
+                    state['exp_avg'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+                    # Exponential moving average of squared gradient values
+                    state['exp_avg_sq'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+                    if amsgrad:
+                        # Maintains max of all exp. moving avg. of sq. grad. values
+                        state['max_exp_avg_sq'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+
+                exp_avgs.append(state['exp_avg'])
+                exp_avg_sqs.append(state['exp_avg_sq'])
+
+                if amsgrad:
+                    max_exp_avg_sqs.append(state['max_exp_avg_sq'])
+
+                state_steps.append(state['step'])
+
+            myadamw(params_with_grad,
+                  grads,
[…]

### 2023-03-08 code/main.py
fix some bugs

@@ -14,7 +14,8 @@ import sys
 
 from myadam import MyAdamW
 
-from models import *
+from resnet import ResNet18
+
 from tqdm import tqdm
 #from torch.utils import progress_bar
 from torch.utils.tensorboard import SummaryWriter
@@ -57,7 +58,7 @@ def test(epoch):
         }
         if not os.path.isdir('checkpoint'):
             os.mkdir('checkpoint')
-        torch.save(state, f'./checkpoint/ckpt{full_name}.pth')
+        torch.save(state, f'./checkpoint/ckpt.pth')
         best_acc = acc
 
 # Training
@@ -132,22 +133,8 @@ if __name__ == '__main__': # protect your program's entry point
     
     # Model
     print('==> Building model..')
-    # net = VGG('VGG19')
     net = ResNet18()
-    # net = PreActResNet18()
-    # net = GoogLeNet()
-    # net = DenseNet121()
-    # net = ResNeXt29_2x64d()
-    # net = MobileNet()
-    # net = MobileNetV2()
-    # net = DPN92()
-    # net = ShuffleNetG2()
-    # net = SENet18()
-    # net = ShuffleNetV2(1)
-    # net = EfficientNetB0()
-    # net = RegNetX_200MF()
-    #net = SimpleDLA()
-    #writer = SummaryWriter('SimpleDla')
+
     net = net.to(device)
     if device == 'cuda':
         net = torch.nn.DataParallel(net)
@@ -162,14 +149,8 @@ if __name__ == '__main__': # protect your program's entry point
         best_acc = checkpoint['acc']
         start_epoch = checkpoint['epoch']
     
-    criterion = nn.CrossEntropyLoss()
-    
-    #optimizer = optim.SGD(net.parameters(), lr=args.lr, momentum=0.9, weight_decay=5e-4)
-    optimizer = MyAdamW(net.parameters(), lr=0.01, betas = (0.9, 0.999), eps=1e-8, weight_decay=2*1e-2)
-    #optimizer = optim.AdamW(net.parameters(), lr=0.01, betas = (0.9, 0.999), eps=1e-8, weight_decay=2*1e-2)
-    
+    criterion = nn.CrossEntropyLoss() 
     num_epoch = 1
-    scheduler = torch.optim.lr_scheduler.CosineAnnealingLR(optimizer, T_max=200)
     
     
     betas = (0.9, 0.999)
@@ -178,12 +159,16 @@ if __name__ == '__main__': # protect your program's entry point
[…]

### 2023-03-08 code/myadam.py

@@ -157,7 +157,7 @@ def _single_tensor_myadamw(params: List[Tensor],
             assert param.is_cuda and step_t.is_cuda, "If capturable=True, params and state_steps must be CUDA tensors."
 
         if torch.is_complex(param):
-            grad = torchex
+            grad = torch.view_as_real(grad)
             exp_avg = torch.view_as_real(exp_avg)
             exp_avg_sq = torch.view_as_real(exp_avg_sq)
             param = torch.view_as_real(param)
@@ -216,8 +216,8 @@ def _single_tensor_myadamw(params: List[Tensor],
             
             ### OUR CHANGING!!!
             tmp = exp_avg + weight_decay * param
-
             param.addcdiv_(tmp, denom, value=-step_size)
+            ###
 
 def _multi_tensor_myadamw(params: List[Tensor],
                         grads: List[Tensor],
@@ -326,3 +326,4 @@ def _multi_tensor_myadamw(params: List[Tensor],
         new_exp_avgs = torch._foreach_add(exp_avgs, wd)
 
         torch._foreach_addcdiv_(params, new_exp_avgs, denom, step_size)
+        ###

### 2023-03-10 paper/main.tex
add new weight decay and graphics

@@
 \section{Introduction}
-In machine learning we consider optimization problem
+In machine learning we consider unconstrained optimization problem
 \begin{equation*}
@@
 
-There are second order preconditioners methods for solving this problem, such as Adam, OASIS, AdaHessian.
+There are second order preconditioners methods for solving this problem, such as Adam \citep{kingma2014adam} , OASIS \citep{}, AdaHessian.
 

### 2023-03-10 code/main.py

@@ -60,6 +60,7 @@ def test(epoch):
             os.mkdir('checkpoint')
         torch.save(state, f'./checkpoint/ckpt.pth')
         best_acc = acc
+    return test_loss, correct, total
 
 # Training
 def train(epoch):
@@ -91,6 +92,7 @@ def train(epoch):
         loop.set_description(f"{full_name} Epoch (Train)[{epoch}/{num_epoch}]")
         loop.set_postfix(loss= train_loss/(batch_idx+1), acc=100.*correct/total, correct=correct, total=total)
 
+    return train_loss, correct, total
 
 if __name__ == '__main__': # protect your program's entry point
 
@@ -155,7 +157,7 @@ if __name__ == '__main__': # protect your program's entry point
     
     betas = (0.9, 0.999)
     learning_rates = [0.1, 0.01, 0.001]
-    weight_decayes = [0.1, 0.01, 0.001]
+    weight_decayes = [0.05, 0.005, 0.0005]
     optimizers = [optim.AdamW, MyAdamW, optim.Adam, optim.SGD]
     names = ['MyAdamW', 'AdamW', 'Adam+L2', 'SGD + L2']
 
@@ -174,7 +176,15 @@ if __name__ == '__main__': # protect your program's entry point
                 writer = SummaryWriter(path)
                 train_step = 0
                 test_step = 0
+                
                 for epoch in range(start_epoch, start_epoch + num_epoch):
-                    train(epoch)
-                    test(epoch)
+                    loss_train, correct_train, total_train = train(epoch)
+                    loss_test, correct_test, total_test = test(epoch)
+
+                    writer.add_scalar('Testing loss (epoch)', loss_test,epoch=epoch)
+                    writer.add_scalar('Testing accuracy (epocj)', 100.*correct_test/total_test, epoch=epoch)
+                    
+                    writer.add_scalar('Training loss (epoch)', loss_train,epoch=epoch)
+                    writer.add_scalar('Training accuracy (epoch)', 100.*correct_train/total_train, epoch=epoch)
+                    
                     scheduler.step()

### 2023-03-10 code/myadam.py

@@ -254,7 +254,7 @@ def _multi_tensor_myadamw(params: List[Tensor],
 
     # Perform stepweight decay
     #torch._foreach_mul_(params, 1 - lr * weight_decay)
-    torch._foreach_mul_(params, 1)
+    #torch._foreach_mul_(params, 1)
     
     # Decay the first and second moment running average coefficient
     torch._foreach_mul_(exp_avgs, beta1)

### 2023-03-21 paper/main.tex
add two theorems

@@
 \usepackage{algpseudocode}
+
+\newtheorem{theorem}{Theorem}
 
@@
 
+\section{Theory}
+To proof this algorigthm we use simplified form of AdamW algorithm
+\begin{algorithm}[H]
+\caption{AdamW}\label{alg:AdamW}
+
+    \begin{algorithmic}
+    \Require{$r, \varepsilon, f$}    
+    \While {$w$ not converged}
+        \State $t = t+1$
+        \State $D_t = \text{diag}(|\nabla f(w_t)|_i)$
+        \State $w_t = w_{t-1} - \eta \cdot \nabla f(w_t) D_t^{-1}  -\lambda \nabla r(w_t)$ 
+    \EndWhile
+\end{algorithmic}
+\end{algorithm}
+
+\begin{theorem}
+
+Suppose the Assumption 1, 2, 5 and let $\varepsilon > 0$ and let the step-size satisfy
+\begin{equation*}
+    \eta < \frac{2 \alpha}{L + l \cdot \alpha} 
+\end{equation*}
+Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem (link here to problem 1) can be bounded by
+\begin{equation*}
+      T = \mathcal{O}\left( \frac{2\Delta_0 \Gamma \alpha } {(2\alpha - \tilde{L}\eta) \eta \varepsilon} \right)
+\end{equation*}
+
+\end{theorem}
+\begin{proof}
+
+Let's write first assumption for step t and $t+1$:
+
+\begin{equation*}
+    f(w_{t+1}) \leq f(w_t) + \langle \nabla f(w_t), w_{t+1} - w_t \rangle + \frac{L}{2}||w_{t+1} - w_t ||^2
+\end{equation*}
+Okay, by definition for our algorithm we have:
+
+\begin{equation*}
+w_{t+1} - w_t = -\eta D_t^{-1} \nabla f(w_t) - \eta \nabla r(w_t)    
+\end{equation*}
+
+and
+
+\begin{equation*}
+\nabla f(w_t) = \frac{1}{\eta} D^t(w_t - w_{t+1}) - D^t \nabla r(w_t)
+\end{equation*}
+
+Okay, now let's replace $\nabla f(w_t)$ and $I \leq \frac{D_t}{\alpha}$
+\begin{equation*}
+    f(w_{t+1}) \leq f(w_t) + \langle \frac{1}{\eta}D_t(w_t - w_{t+1}) - D_t\nabla r(w_t), w_{t+1} - w_t \rangle + \frac{L}{2 \alpha} ||w_{t+1} - w_t||_{D_t}^2
+\end{equation*}
+
+\begin{equation*}
+    f(w_{t+1}) \leq f(w_t) + \left(\frac{L}{2 \alpha} - \frac{1}{\eta} \right) ||w_{t+1} - w_t||_{D_t}^2 - \langle D_t \nabla r(w_t), w_{t+1} - w_t \rangle
+\end{equation*}
+
+Lets define new variable $\tilde{r} : \nabla \tilde{r} = D_t \nabla r(w_t)$. Then rewrite step using the variable and 5-th assumption.
+\begin{equation*}
+    \tilde{r}(w_{t+1}) \leq \tilde{r}(w_t) + \langle \tilde{r}(w_t), w_{t+1} - w_t \rangle + \frac{l}{2} (w_{t+1} - w_t)^T D_t (w_{t+1} - w_t)
+\end{equation*}
+
+\begin{equation*}
+    f(w_{t+1}) \leq f(w_t) + \left( \frac{L}{2\alpha} - \frac{1}{\eta} \right) ||w_{t+1} - w_t||_{D_t}^2 + \tilde{r}(w_t) - \tilde{r}(w_{t+1}) + \frac{l}{2}||w_{t+1}-w_t||_{D_t}^2
+\end{equation*}
+
+$\tilde{F}(w) = f(w) + \tilde{r}(w)$, $F(w) = f(w) + r(w)$, ($\tilde{L}=L + l \alpha$), we get:
+
+\begin{equation*}
+    \tilde{F}(w_{t+1}) \leq \tilde{F}(w_t) + \left( \frac{\tilde{L}}{2\alpha} - \frac{1}{\eta}  \right) ||w_{t+1} - w_t||_{D_t}^2
+\end{equation*}
+
+\begin{equation*}
+    \left(\frac{1}{\eta} - \frac{\tilde{L}}{2\alpha}   \right) ||w_{t+1} - w_t||_{D_t}^2 \leq \tilde{F}(w_t) - \tilde{F}(w_{t+1})
+\end{equation*}
+
+\begin{equation*}
+    \frac{\eta^2  (T+1)}{\Gamma}\left(\frac{1}{\eta} - \frac{\tilde{L}}{2\alpha}   \right)\cdot\min_{k = 0, T} ||\nabla f(w_t) + \nabla \tilde{r}(w_t)||^2 \leq \frac{\eta^2}{\Gamma}\left(\frac{1}{\eta} - \frac{\tilde{L}}{2\alpha}   \right)\cdot\sum\limits_{t = 0}^T ||\nabla f(w_t) + \nabla \tilde{r}(w_t)||^2 \leq \tilde{F}(w_0) - \tilde{F}(w_*)
+\end{equation*}
+
+\begin{equation*}
+    \min_{t = 0, T} ||\nabla f(w_t) + \nabla \tilde{r}(w_t)||^2 \leq \frac{(\tilde{F}(w_0) - \tilde{F}(w_*))\Gamma}{(\frac{1}{\eta} - \frac{\tilde{L}}{2\alpha}) \eta^2 (T+1)} = \varepsilon
+\end{equation*}
+
+\begin{equation*}
+    T + 1 \geq \frac{\Delta_0 \Gamma}{(\frac{1}{\eta} - \frac{\tilde{L}}{2\alpha}) \eta^2 \varepsilon}
+\end{equation*}
+
+Then:
+\begin{equation*}
+      T = \mathcal{O}\left( \frac{2\Delta_0 \Gamma \alpha } {(2\alpha - \tilde{L}\eta) \eta \varepsilon} \right)
+\end{equation*}
+\end{proof}
+
+\begin{theorem}
+    Suppose the Assumption 1, 2, 4, 5 and let $\varepsilon > 0$ and let the step-size satisfy
+    \begin{equation*}
+        \eta \leq \frac{2 \alpha}{\tilde{L}}
+    \end{equation*}
+    Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem (link here to problem 1) can be bounded by
+    \begin{equation*}
+        T =  \mathcal{O}\left( \frac{\ln \frac{\Delta_0}{\epsilon}}{2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha})} \right)
+    \end{equation*}
+\end{theorem}
+
+\begin{proof}
+    Assume 
+    \begin{equation}
+    \nabla \tilde{F} = \nabla f + \nabla \tilde{r}    
+    \end{equation}
+
+    \begin{equation}
+    L + ||D_t||l = \tilde{L}        
+    \end{equation}
+    \begin{equation*}
+    w_{t+1} - w_t = -\eta D_t^{-1} \nabla r(w_t) - \eta \nabla r(w_t) = -\eta D_t^{-1} (\nabla f + \nabla \tilde{r})(w_t) = -\eta D_t^{-1} \nabla \tilde{F}(w_t)    
+    \end{equation*}
+    Then we write $\tilde{L}$-smoothness for $\tilde{F}$ 
+    \begin{equation*}
+        \tilde{F}(w_{t+1}) - \tilde{F}(w_t) \leq  \langle \nabla \tilde{F}(w_t), w_{t+1} - w_t \rangle + \frac{\tilde{L}}{2} ||w_{t+1} - w_t||^2
+    \end{equation*}
+    \begin{equation*}
+        \tilde{F}(w_{t+1}) - \tilde{F}(w_t) \leq - \langle \frac{1}{\eta} D_t(w_{t+1} - w_t), w_{t+1} - w_t \rangle + \frac{\tilde{L}}{2} ||w_{t+1} - w_t||^2 = (\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) ||w_{t+1} - w_t||^2_{D_t}
+    \end{equation*}
+    \begin{equation*}
+        = (\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) ||w_{t+1} - w_t||^2_{D_t} = (\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) ||-\eta D_t^{-1} \nabla \tilde{F}(w_t)||_{D_t}^2  \leq (\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) \eta^2 ||\nabla \tilde{F}(w_t)||^2_{D_t^{-1}}
+    \end{equation*}
+    Then we use PL-condition for the function $\tilde{F}$:
+    \begin{equation*}
+        ||\nabla \tilde{F}(w_t)||_{D_t^{-1}}^2 \geq 2 \mu (\tilde{F}(w_t) - \tilde{F}^*)
+    \end{equation*}
+
+    \begin{equation*}
+    \tilde{F}(w_{t}) -  F^* \ge \tilde{F}(w_{t+1}) - \tilde{F}^* + (\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}) \eta^2 2 \mu (\tilde{F}(w_t) - \tilde{F}^*) = \left( 1 +  2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}) \right) (\tilde{F}(w_{t+1}) - \tilde{F}^*)
+    \end{equation*}
+
+    \begin{equation*}
+    \epsilon \ge \Delta_0 \left( 1 +  2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}) \right)^{-T} \ge (\tilde{F}(w_{T}) - \tilde{F}^*)        
+    \end{equation*}
+
+    \begin{equation*}
+    T = \frac{\ln \frac{\Delta_0}{\epsilon}}{\ln(1 + 2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}))} \approx \frac{\ln \frac{\Delta_0}{\epsilon}}{2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha})}
+    \end{equation*}
+    Then:
+    \begin{equation*}
+    T =  \mathcal{O}\left( \frac{\ln \frac{\Delta_0}{\epsilon}}{2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha})} \right)
+    \end{equation*}
+\end{proof}
+
 \bibliographystyle{unsrtnat}

### 2023-03-21 code/myadam.py

@@ -214,10 +214,32 @@ def _single_tensor_myadamw(params: List[Tensor],
             else:
                 denom = (exp_avg_sq.sqrt() / bias_correction2_sqrt).add_(eps)
             
-            ### OUR CHANGING!!!
-            tmp = exp_avg + weight_decay * param
-            param.addcdiv_(tmp, denom, value=-step_size)
-            ###
+            
+            ### PROBABILITY ALGORITHM!!! ###
+            vera = torch.randint(0, 3, (1,))
+            if int(vera) == 0:
+                # под гессиан
+                ### OUR CHANGING!!!
+                tmp = exp_avg + weight_decay * param
+                param.addcdiv_(tmp, denom, value=-step_size)
+                ###
+            elif int(vera) == 1:
+                # и туда и сюда
+                ### OUR CHANGING!!!
+                param.mul_(1 - lr * weight_decay)
+                tmp = exp_avg + weight_decay * param
+                param.addcdiv_(tmp, denom, value=-step_size)
+                ###
+            elif int(vera) == 2:
+                # только снаружи
+                ### OUR CHANGING!!!
+                param.mul_(1 - lr * weight_decay)
+                param.addcdiv_(exp_avg, denom, value=-step_size)
+                ###
+            elif int(vera) == 3:
+                param.addcdiv_(exp_avg, denom, value=-step_size)
+
+            
 
 def _multi_tensor_myadamw(params: List[Tensor],
                         grads: List[Tensor],
@@ -321,9 +343,38 @@ def _multi_tensor_myadamw(params: List[Tensor],
             torch._foreach_div_(exp_avg_sq_sqrt, bias_correction2_sqrt)
             denom = torch._foreach_add(exp_avg_sq_sqrt, eps)
         
+        ''' LAST CENTURY TECHNOLOGY
         ### OUR CHANGING!
         wd = torch._foreach_mul(params, weight_decay)
         new_exp_avgs = torch._foreach_add(exp_avgs, wd)
 
         torch._foreach_addcdiv_(params, new_exp_avgs, denom, step_size)
         ###
+        '''
+
+        ### PROBABILITY ALGORITHM!!! ###
+        vera = torch.randint(0, 3, (1,))
+        if int(vera) == 0:
+            # под гессиан
+            ### OUR CHANGING!!!
+            wd = torch._foreach_mul(params, weight_decay)
+            new_exp_avgs = torch._foreach_add(exp_avgs, wd)
[…]

### 2023-03-29 paper/main.tex
change abstract and add cites for methods

@@
 In machine learning we consider unconstrained optimization problem
-\begin{equation*}
+\begin{equation}
 	\min_{w \in \mathbb{R}^d} f(w)
-\end{equation*}
+\end{equation}
 Problems of the form (1) cover a plethora of applications, including empirical risk minimization,
-deep learning, and supervised learning tasks such as regularized least squares or logistic regression. This minimization problem can be difficult to solve, particularly when the number of training
+deep learning \citep{lecun2015deep}, and supervised learning \citep{cunningham2008supervised} tasks such as regularized least squares \citep{rifkin2007notes} or logistic regression \citep{shalev2014understanding}.
+This minimization problem can be difficult to solve, particularly when the number of training
 samples n, or problem dimension d, is large, or if the problem is nonconvex.
 
-There are second order preconditioners methods for solving this problem, such as Adam \citep{kingma2014adam} , OASIS \citep{}, AdaHessian.
+Second order preconditioners methods are methods when instead of calculate true hessian of our function for newton method \citep{dennis1977quasi}, some heuristics is used to calculate pseudo-hessian.
+There are second order preconditioners methods for solving this problem, such as Adam \citep{kingma2014adam} , OASIS \citep{goldberg2011oasis}, AdaHessian \citep{yao2021adahessian}.
 
@@
 \section{Problem statement}
+
 We consider the unconstrained optimization problem

### 2023-03-29 code/myadam.py

@@ -212,7 +212,10 @@ def _single_tensor_myadamw(params: List[Tensor],
                 # Use the max. for normalizing running avg. of gradient
                 denom = (max_exp_avg_sqs[i].sqrt() / bias_correction2_sqrt).add_(eps)
             else:
+                
                 denom = (exp_avg_sq.sqrt() / bias_correction2_sqrt).add_(eps)
+                tmp_wd = torch.ones_like(denom) * weight_decay
+                denom = torch.maximum(denom, tmp_wd)
             
             
             ### PROBABILITY ALGORITHM!!! ###
@@ -342,6 +345,10 @@ def _multi_tensor_myadamw(params: List[Tensor],
             exp_avg_sq_sqrt = torch._foreach_sqrt(exp_avg_sqs)
             torch._foreach_div_(exp_avg_sq_sqrt, bias_correction2_sqrt)
             denom = torch._foreach_add(exp_avg_sq_sqrt, eps)
+            
+            ###
+            torch._foreach_maximum_(exp_avg_sq_sqrt, exp_avg_sqs)
+            
         
         ''' LAST CENTURY TECHNOLOGY
         ### OUR CHANGING!

### 2023-03-30 paper/main.tex
Add files via upload

@@
 \section{Problem statement}
+We want to investigate the convergence speed of the AdamW method and the newly proposed MyAdamW method in machine learning problems, and we also plan to prove the convergence of these methods and investigate the obtained solution.
 
@@
 \end{equation*}
-Problems of the form cover a plethora of applications, including empirical risk minimization,
-deep learning, and supervised learning tasks such as regularized least squares or logistic regression.
 
@@
 
-For solving these problems we always scaled adaptive gradients algorithms like ADAM, OASIS, ADAHessian.
-We investigate how the convergence rate will change when the regularization function is added to these algorithms.
-
-% В исследуемом нами алгоритме сходимости мы будем исследовать алгоритмы двух следующих видов.
-В первом функция регуляризации выносится отдельном в пересчете весов модели, во втором функция домножается на обратный "гессиан".
 In the convergence algorithm that we study, we will investigate algorithms of the following two kinds.

### 2023-04-12 paper/main.tex
update paper and code before review

@@
 \usepackage{algpseudocode}
+
+% Цвета 
+\usepackage{xcolor}
+\usepackage{color}
+\usepackage{colortbl}
 
@@
 deep learning \citep{lecun2015deep}, and supervised learning \citep{cunningham2008supervised} tasks such as regularized least squares \citep{rifkin2007notes} or logistic regression \citep{shalev2014understanding}.
-This minimization problem can be difficult to solve, particularly when the number of training
-samples n, or problem dimension d, is large, or if the problem is nonconvex.
 
-Second order preconditioners methods are methods when instead of calculate true hessian of our function for newton method \citep{dennis1977quasi}, some heuristics is used to calculate pseudo-hessian.
-There are second order preconditioners methods for solving this problem, such as Adam \citep{kingma2014adam} , OASIS \citep{goldberg2011oasis}, AdaHessian \citep{yao2021adahessian}.
+The classic base method for solving the optimization is gradient descent, but this minimization problem can be difficult to solve, particularly when the number of training samples n, or problem dimension d, is large.
+In modern machine learning especially large problems represent the greatest interest.
+For such cases stochastic gradient descent \citep{bottou2010large} became popular solution.
+Despite its simplicity, it proved itself to be an efficient and effective optimization method.
+For a long time first-ordered methods were most popular approach of solving optimization problems.
 
-Throughout this work we assume that each f $:\mathbb{R}^d \rightarrow \mathbb{R}$ is twice differentiable and also L-smooth. This is formalized in the following assumption.
+Other way of solving the problem are methods with adaptive gradient \citep{wilson2017marginal}. These methods posses several superiority over first-ordered methods.
+Firstly, they have bigger potential of distributed solving, because first ordered methods spend majority of time on "communication".
+Secondly, they are less sensitive to the choice of hyperparameters up to the point that hyperparameters can be set equal to one.
+Lastly, this methods often simply show faster convergence on modern large optimization problems, especially this methods became applicable in neural networks solving.
+Nowadays it is known that preconditioning methods often outperform other methods on modern large optimization problems \citep{zhang2018three, yao2021adahessian, kingma2014adam, goldberg2011oasis}.
 
+Preconditioning methods refer to techniques that involve scaling the gradient of a problem by a specific matrix $D_t$, which enables the gradient to take into account the geometry of the problem.
+In the classical case $D_t = (\nabla^2 f)^{-1}$, which corresponds newton's method, however hessian is difficult to calculate and even more difficult to reverse, because of that some heuristics are used to replace the reversed hessian \citep{dennis1977quasi}.
+In OASIS \citep{goldberg2011oasis} or AdaHessian \citep{yao2021adahessian} hessian is assumed to have diagonal dominance.
+In Adam \citep{kingma2014adam} gradient is simply normalized, etc.
+This heuristics were proved to be effective and efficient.
+General scheme of methods with preconditioning can be framed in the following algorithm
+
+% записать в одну строчку, и пояснить g_t, D_t^{-1}
+\begin{algorithm}[H]
+
+            \caption{General scheme for preconditions methods}\label{alg:genalg}
+
+            \begin{algorithmic}
+            \small{
+            \Require{$\eta, f$}
+
+            \While {$w$ not converged}
+            \State $t = t+1$
+            \State $g_t \gets \nabla f(w_{t-1})$
+            \State $D_t \gets$ pseudo-hessian, precondtioning, scaling
+            \State $w_t = w_{t-1} - \eta \cdot g_t D_t^{-1}$    
+            \EndWhile
+            }
+\end{algorithmic}
+\end{algorithm}
+
+Regularization is a powerful technique in machine learning that aims to prevent overfitting by adding additional constraints to the model.
+It has been widely applied to various machine learning problems, including image classification, speech recognition, and natural language processing, and has shown its effectiveness in improving the generalization capability of neural networks \citep{poggio1987computational}.
+
+In methods with preconditioning appears to be several ways to include regularization.
+We can include regularizer $r$ in $g_t$ calculation so it will be taken into consideration while calculating $D_t$. This method is equal to considering optimization problem
+
+\begin{equation}
+	\min_{w \in \mathbb{R}^d} f(w) + r(w).
+\end{equation}
+
+Or we can include regularizer only on last step, decreasing norm of $w$ \citep{loshchilov2017decoupled}.
+This way of regularization is called weight decay and surprisingly turns out to be more efficient in practical problems.
+There are few other ways of considering regularizer which will be discussed further in the paper.
+
+In general, our paper provides insight into comparison of different consideration ways of regularization is methods with preconditioning. Here, we provide a brief summary of our main contributions:
+
+\begin{itemize}
+    \item \textbf{Proof of preconditioned methods' with weight decay convergence}.
+We derive convergence guarantees for preconditioned methods considering assumptions of smoothness, strongly convex and PL-condition.
+
+    \item \textbf{Research of the loss function} Comparison of accuracy and loss function for AdamW and AdamL2. As a result we saw that AdamW asymptotically converges to a non-zero value
+
+    \item \textbf{Competitive Numerical Results} We investigate the empirical performance of Adam's variation including new one on a variety of standard machine learning tasks, including logistic regression.
+\end{itemize}
+
+\section{Problem statement}
+We want to investigate the convergence speed of the AdamW method and the newly proposed MyAdamW method in machine learning problems, and we also plan to prove the convergence of these methods and investigate the obtained solution.
+
+We consider the unconstrained optimization problem
+\begin{equation*}
+	\min_{w \in \mathbb{R}^d} f(w)
+\end{equation*}
+
+But we can add regulirazation $r(w)$ -- regularization, and solve the unconstrained optimization problem.
+\begin{equation*}
+	\min_{w \in \mathbb{R}^d} F(w) = f(w) + r(w)
+\end{equation*}
+
+In the convergence algorithm that we study, we will investigate algorithms of the following two kinds.
+In the first one, the regularization function is taken out separately in the recalculation of model weights, and in the second one, the function is dominated by the inverse "hessian".
+
+\begin{algorithm}[H]
+
+    \caption{General scheme for preconditions methods}\label{alg:genalg}
+
+    \begin{algorithmic}
+    \small{
+    \Require{$\eta, \epsilon, f, r$}
+
+    \While {$w$ not converged}
+    \State $t = t+1$
+    \State $g_t = \nabla f_t(w_{t-1})$
+    \State $D_t =$ \textcolor{red}{diag($\sqrt{g_t \odot g_t} + \varepsilon$)}  \hfill \textcolor{red}{AdamW}
+    \State $D_t$ = \textcolor{cyan}{$\mathbb{E}[z^T \nabla^2f(w_{t-1}) z]$} \hfill \textcolor{violet}{OASIS}, where $z$ in Rademacher distribution
+    \State $w_t = w_{t-1} - \eta \cdot g_t D_t^{-1}$    
+    \EndWhile
+    }
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[H]
+
+    \caption{Adam($\lambda$)}\label{alg:Adam}
+
+    \begin{algorithmic}
+    \small{
+    \Require{$\eta, \beta_1, \beta_2, \epsilon, f, r$}
+    %\State $m_0 = 0$ -- 1-st moment vector
+    %\State$v_0 = 0$ -- 2-nd moment vector
+    \While {$\theta$ not converged}
+    \State $t = t+1$
+    \State $g_t = \nabla f(w_{t-1})$ + \textcolor{blue}{$\nabla r(w_{t-1})$} \hfill \textcolor{blue}{AdamL2}    
+    \State $m_t = \beta_1 \cdot m_{t-1} + (1 - \beta_1) \cdot g_t$
+    \State $v_t = \beta_2 \cdot v_{t-1} + (1 - \beta_2) \cdot g_t^2$
+    \State $\hat{m_t} = \frac{m_t}{1-\beta_1^t}$ + \textcolor{green}{$\nabla r(w_{t-1})$} \hfill \textcolor{green}{MyAdamW}
+    \State $\hat{v_t} = \frac{v_t}{1-\beta_2^t}$ 
+    \State $w_t = w_{t-1} - \eta \cdot \frac{\hat{m_t}}{\sqrt{v_t} + \epsilon}$    - \textcolor{red}{$\eta \nabla r(w_{t-1})$ } \hfill \textcolor{red}{AdamW}
+    \EndWhile
+    }
+\end{algorithmic}
+\end{algorithm}
+
+\section{Experiment}
+% Мы проведем эксперимент, в котором сравним Adam с добавленной L2 регуляризацией с AdamW, при различных learning rate и decoupled weight, также мы сравним его с измененным алгоритмом AdamW, где регуляризатор занесен под гессиан, также мы сравним его при условии, что теперь минимальное собственное число гессиана, это не epsilon, а гиперпараметр decoupled weight.Проведем те же эксперименты со SGD и L2 регуляризацией и SGD с decoupled weitght при тех же параметрах.
+Все эксперименты будут проводиться на батчах размера 128, на сетке ResNet18, в 200 эпох.
+Всё это будет реализовано с помощью библиотеки PyTorch на dataset CIFAR10.
+
+We will conduct an experiment in which we compare Adam with added L2 regularization with AdamW, at different learning rate and decoupled weight, also we will compare it with the modified AdamW algorithm where the regularizer is put under the hessian, also we will compare it under the condition that now the minimal eigenvalue of hessian is not epsilon, but decoupled weight hyperparameter.We will conduct the same experiments with SGD and L2 regularization and SGD with decoupled weitght at the same parameters.
+All experiments will be performed on batches of size 128, on a ResNet18 grid of 200 epochs.
+All this will be implemented using the PyTorch library on dataset CIFAR10.
+
+\section{Theory}
 \begin{assumption}{1}{Convex}
@@
 	\end{equation*}
-
 \end{assumption}
 
-\section{Problem statement}
-We want to investigate the convergence speed of the AdamW method and the newly proposed MyAdamW method in machine learning problems, and we also plan to prove the convergence of these methods and investigate the obtained solution.
-
-We consider the unconstrained optimization problem
-\begin{equation*}
-	\min_{w \in \mathbb{R}^d} f(w)
-\end{equation*}
-
-But we can add regulirazation $r(w)$ -- regularization, and solve the unconstrained optimization problem.
-\begin{equation*}
-	\min_{w \in \mathbb{R}^d} F(w) = f(w) + r(w)
-\end{equation*}
-
-In the convergence algorithm that we study, we will investigate algorithms of the following two kinds.
-In the first one, the regularization function is taken out separately in the recalculation of model weights, and in the second one, the function is dominated by the inverse "hessian".
-
-\begin{algorithm}[H]
-	\caption{Based algorithm}\label{alg:Based}
-	$w_0, D_0, \eta_0$
-	\begin{algorithmic}
-		\For{$k = 1, 2, ...$}
-		\State $D_k$ - update by using information of $f(w)$
-		\State $\eta_k$ - update
-		\State Set $w_{k+1} = w_k - \eta_k D_k^{-1} \nabla f(w_k) - \eta \nabla r(w)$ 
-		\State or like that
-		\State Set $w_{k+1} = w_k - \eta_k D_k^{-1} (\nabla f(w_k) + \nabla r(w))$
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
-\section{Experiment}
-% Мы проведем эксперимент, в котором сравним Adam с добавленной L2 регуляризацией с AdamW, при различных learning rate и decoupled weight, также мы сравним его с измененным алгоритмом AdamW, где регуляризатор занесен под гессиан, также мы сравним его при условии, что теперь минимальное собственное число гессиана, это не epsilon, а гиперпараметр decoupled weight.Проведем те же эксперименты со SGD и L2 регуляризацией и SGD с decoupled weitght при тех же параметрах.
-Все эксперименты будут проводиться на батчах размера 128, на сетке ResNet18, в 200 эпох.
-Всё это будет реализовано с помощью библиотеки PyTorch на dataset CIFAR10.
-
-We will conduct an experiment in which we compare Adam with added L2 regularization with AdamW, at different learning rate and decoupled weight, also we will compare it with the modified AdamW algorithm where the regularizer is put under the hessian, also we will compare it under the condition that now the minimal eigenvalue of hessian is not epsilon, but decoupled weight hyperparameter.We will conduct the same experiments with SGD and L2 regularization and SGD with decoupled weitght at the same parameters.
-All experiments will be performed on batches of size 128, on a ResNet18 grid of 200 epochs.
-All this will be implemented using the PyTorch library on dataset CIFAR10.
-
-\section{Theory}
 To proof this algorigthm we use simplified form of AdamW algorithm
@@
 \end{theorem}
+
+\begin{theorem}
+    Suppose the Assumption 1, 2, 4, 5 and let $\varepsilon > 0$ and let the step-size satisfy
+    \begin{equation*}
+        \eta \leq \frac{2 \alpha}{\tilde{L}}
+    \end{equation*}
+    Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem (link here to problem 1) can be bounded by
+    \begin{equation*}
+        T =  \mathcal{O}\left( \frac{\ln \frac{\Delta_0}{\epsilon}}{2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha})} \right)
+    \end{equation*}
+\end{theorem}
+\section{Appendix}
+
+\begin{theorem}
+Suppose the Assumption 1, 2, 5 and let $\varepsilon > 0$ and let the step-size satisfy
+\begin{equation*}
+    \eta < \frac{2 \alpha}{L + l \cdot \alpha} 
+\end{equation*}
+Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem (link here to problem 1) can be bounded by
+\begin{equation*}
+      T = \mathcal{O}\left( \frac{2\Delta_0 \Gamma \alpha } {(2\alpha - \tilde{L}\eta) \eta \varepsilon} \right)
+\end{equation*}
+
+\end{theorem}
+
 \begin{proof}

### 2023-04-12 code/lib.py

@@ -1,0 +1,295 @@
+#@title Класс логистической регрессии
+import numpy as np
+import scipy.linalg as la
+import random
+from sklearn.metrics import accuracy_score
+from datetime import datetime as dt
+from tqdm import tqdm
+
+class MyLogregression:
+    def __init__(self, fit_intercept=False, eps=5*1e-3,     iter =10 ** 3, batch=False, batch_size=50, decreasing_lr=False, name="GD", lr_func = None, label="None", dependent=False, l2_coef=0, betas = [0.999, 0.99]):
+        self.fit_intercept = fit_intercept
+        self._iter         = iter
+        self._batch        = batch
+        self._eps          = eps
+        self._opt          = self.choose_opt_method(name)
+        self._name         = name
+        self._batch_size   = batch_size
+        self._decreasing_lr = decreasing_lr
+        self._lr_func      = lr_func 
+        self._label        = label
+        self._dependent    = dependent
+        self._l2_coef      = l2_coef
+        self._betas        = betas
+        self._grad_function = self.__grad_function
+        if name == "AdamL2" or name == "AdamW":
+            self._error_criterion = lambda w: np.linalg.norm(self._grad_function(w) + self._l2_coef * w, 2)
+        else:
+            self._error_criterion = lambda w: np.linalg.norm(self._grad_function(w), 2)
+        self._to_seconds = lambda s: s.microseconds * 1e-6 + s.seconds
+    
+    def __function(self, w):
+        sum = 0
+        n = self._X_train.shape[0]
+
+        for i in range(len(self._y_train)):     
+            sum = sum + 1/n * np.log(1 + np.exp(-self._y_train[i] * self._X_train[i, :] @ w)) 
+        
+        return sum
+    
+    def __grad_function(self, w):
+        sum = np.zeros(w.shape)
+        n = self._X_train.shape[0]
+        
+        for i in range(len(self._y_train)):            
+            up = self._y_train[i] * self._X_train[i] * np.exp(-self._y_train[i] * w * self._X_train[i])
+            down = n * (1 + np.exp(-self._y_train[i] * w * self._X_train[i]))
+            sum = sum  - up/down
+
+        return sum
+
+    def __add_constant_column(self, X):
+        n, k = X.shape
+        if self.fit_intercept:
+            X_train = np.hstack((X, np.ones((n, 1))))
+            #w0 = np.random.rand(k+1)
+            w0 = np.zeros(k+1)
[…]

### 2023-04-12 code/main.py

@@ -1,183 +1,0 @@
-'''Train CIFAR10 with PyTorch.'''
-import torch
-import torch.nn as nn
-import torch.optim as optim
-import torch.nn.functional as F
-import torch.backends.cudnn as cudnn
-
-import torchvision
-import torchvision.transforms as transforms
-
-import os
-import argparse
-import sys
-
-from myadam import MyAdamW
-
-from resnet import ResNet18
-
-from tqdm import tqdm
-#from torch.utils import progress_bar
-from torch.utils.tensorboard import SummaryWriter
-
-
-def test(epoch):
-    global best_acc
-    global test_step
-    net.eval()
-    test_loss = 0
-    correct = 0
-    total = 0
-    with torch.no_grad():
-        loop = tqdm(enumerate(testloader), total=len(testloader), leave=False)
-        for batch_idx, (inputs, targets) in loop:
-            test_step += 1
-            inputs, targets = inputs.to(device), targets.to(device)
-            outputs = net(inputs)
-            loss = criterion(outputs, targets)
-
-            test_loss += loss.item()
-            _, predicted = outputs.max(1)
-            total += targets.size(0)
-            correct += predicted.eq(targets).sum().item()
-            
-            writer.add_scalar('Testing loss', test_loss/(batch_idx+1),global_step=test_step)
-            writer.add_scalar('Testing accuracy', 100.*correct/total, global_step=test_step)
-            
-            loop.set_description(f"{full_name}Epoch (Test)[{epoch}/{num_epoch}]")
-            loop.set_postfix(loss= test_loss/(batch_idx+1), acc=100.*correct/total,correct=correct, total=total)
-
-    # Save checkpoint.
-    acc = 100.*correct/total
-    if acc > best_acc:
-        print('Saving..')
-        state = {
-            'net': net.state_dict(),
-            'acc': acc,
-            'epoch': epoch,
-        }
-        if not os.path.isdir('checkpoint'):
-            os.mkdir('checkpoint')
-        torch.save(state, f'./checkpoint/ckpt.pth')
-        best_acc = acc
-    return test_loss, correct, total
-
-# Training
-def train(epoch):
-    #print('\nEpoch: %d' % epoch)
-    global train_step
-    net.train()
-    train_loss = 0
-    correct = 0
-    total = 0
-    loop = tqdm(enumerate(trainloader), total=len(trainloader), leave=False)
-    
-    for batch_idx, (inputs, targets) in loop:
-        inputs, targets = inputs.to(device), targets.to(device)
[…]

### 2023-04-12 doc/review.tex
add review on Nikita's article

\documentclass[17pt]{ article}

\usepackage[utf8]{inputenc}
\usepackage[english, russian]{babel}
\usepackage[T1]{fontenc}

\begin{document}

\begin{center}
    Рецензия на рукопись.

    Дистилляция моделей и данных.

    Баринов Н.
\end{center}

\subsection*{Статья:}
\begin{itemize}

\item Introduction написан хорошо, мне нравится.

\item В пункте 3.1 дистилляция данных мне непонятно, $\theta_t^* := \theta_t^*$, т.к. там написано, что инициализируем случаным значением параметры модели-студента, нужно поправить обозначения.

\item В пункте 3.2 Дистилляция моделей совсем не понятна форма записи функции потерь, наверное, стоит пояснить её.

\item В пункте 3.3 не написана новая функция потерь.

\item В пункте 4.1 в таблице пропущено значение для ConvNet, хотя эксперименты для неё проведены.

\item Вывода пока нет

\end{itemize}

\subsection*{Графики:}
Стоит сохранить картинки, а не делать скриншоты, это сильно портит качество картинок.

Можно зарегестрироваться на kaggle, чтобы проделать более масштабные эксперименты с большим количеством эпох, 30 часов вычислительной мощности в неделю это позволяет. Я делал там, это удобно.

\subsection*{Код:}
\begin{itemize}
    \item Модуль networks не загружен на github.
    \item В статье идет речь об экспериментах только на CIFAR10, внутри есть ещё код для экспериментов на MNIST, может быть ещё не добавили или уже убрали.
    \item Код понятный, читаемый, эксперимент воспроизводится, нужно убрать импорт из networks, т.к. модели уже были добавлены в файл, а не импортируется из модуля.
\end{itemize}

Рецензент:
\newline Крейнин М.В.

\end{document}

### 2023-04-12 paper/main.tex
add review on Nikita's article

@@
 
+The OASIS algorithm differs from Adam in that it updates the learning rate and calculates the pseudo-Hessian matrix at each step using the expectation and a random variable distributed according to the Rademacher distribution.
+
+This is OASIS, the main difference from Adam is how the Hessian is considered, but when proving convergence, this will not play any role.
+\begin{algorithm}[H]
+\caption{OASIS}\label{alg:OASIS}
+\begin{algorithmic}
+    \Require{$w_0, \eta_0, D_0, \theta_0 = + \infty$}    
+    \State $w_1 = w_0 - \eta \hat{D_0}^{-1} \nabla F(w_0)$
+
+    \For{$k = 1, 2, ...$}
+    \State $D_k = \beta D_{k-1} + (1-\beta_2) \cdot diag\left( z_k \odot \nabla^2 F(w_k) z_k \right)$
+    \State $(\hat{D_k})_{ii} = max \{|D_k|_{i, i} ; \alpha \}$, $\forall i = \overline{1, d}$
+    \State $\eta_k = min \{ \sqrt{1 + \theta_{k-1}} \cdot \eta_{k-1}; \frac{||w_k - w_{k-1}||_{\hat{D_k}}}{2 ||\nabla F(w_k) - \nabla F(w_{k-1}) ||_{\hat{D_k}}^* } \}$
+    \State $\theta_k = \frac{\eta_k}{\eta_{k-1}}$
+    \EndFor
+
+\end{algorithmic}
+\end{algorithm}
+
+Now we will show the main differences between the methods of AdamL2, AdamW and MyAdamW -- the algorithm that we propose in this article
+
 \begin{algorithm}[H]
@@
 \end{theorem}
+
+\bibliographystyle{unsrtnat}
+\bibliography{references}
 \section{Appendix}
@@
 
-\bibliographystyle{unsrtnat}
-\bibliography{references}
-
 \end{document}

### 2023-04-12 doc/distillation.py

@@ -1,0 +1,841 @@
+# -*- coding: utf-8 -*-
+"""Dist_big_little_basedist.ipynb
+
+Automatically generated by Colaboratory.
+
+Original file is located at
+    https://colab.research.google.com/drive/1hsHl5xixfnrCzLXZKnjL3LTsYRigwpMF
+"""
+
+# Commented out IPython magic to ensure Python compatibility.
+import torch
+import torch.nn as nn
+
+import torchvision
+import torchvision.transforms as transforms
+
+from tqdm.notebook import tqdm
+
+import matplotlib.pyplot as plt
+from IPython.display import clear_output
+
+from math import ceil, sqrt
+
+from torch.utils.data import Dataset
+from torchvision import datasets
+
+# On top of dataset for batching, shuffle, ...
+from torch.utils.data import DataLoader
+
+# Augumentations for images
+from torchvision import transforms as tr
+
+
+import torch.nn.functional as F
+
+import numpy as np
+import random
+
+import warnings
+warnings.filterwarnings("ignore")
+# autoreload ALL modules in real time
+# %load_ext autoreload
+# %autoreload 2
+
+#########
+# FIXIT #
+#########
+from networks import ConvNet
+
+from utils import get_dataset, get_network, get_eval_pool, evaluate_synset, get_time, DiffAugment, ParamDiffAug, get_default_convnet_setting
+
+!pip install kornia
+
+# Section of setting seeds for reproducible results of training CNNs
+
+# Set the seed for the Python random module
+random.seed(0)
+
+# Set the seed for NumPy's random number generator
+np.random.seed(1)
+
+# Set the seed for PyTorch's random number generator
+torch.manual_seed(2)
+
+# If training on GPU, set the seed for the GPU backend and CUDA library
+if torch.cuda.is_available():
+    torch.cuda.manual_seed_all(3)
+
+g = torch.Generator()
+g.manual_seed(4)
+
+def show_images(images, labels=None, title=None, transform=None, figsize=(12, 12)):
+    fig = plt.figure(figsize=figsize, linewidth=5)
+    grid_val = ceil(sqrt(len(images)))
+    grid_specs = plt.GridSpec(grid_val, grid_val)
+    
+    for i, image in enumerate(images):
+        ax = fig.add_subplot(grid_specs[i // grid_val, i % grid_val])
+        ax.axis('off')
+        
+        if transform is not None:
+            image = transform(image)
+        
+        if labels is not None:
[…]

### 2023-04-22 paper/main.tex
edit paper

--- 2023-03-30 paper/main.tex
@@
 \documentclass{article}
+
 \usepackage{arxiv}
 
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\usepackage{url}
-\usepackage{booktabs}
-\usepackage{amsfonts}
-\usepackage{nicefrac}
-\usepackage{microtype}
-\usepackage{lipsum}
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[english]{babel}	% локализация и переносы
+%\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+\usepackage{lipsum}		% Can be removed after putting your text content
 \usepackage{graphicx}
@@
 \usepackage{amsthm}
+\usepackage{amssymb}
+\usepackage{mathtools}
 \usepackage{algorithm}
 \usepackage{algpseudocode}
+
+\graphicspath{{pictures/}, {images/}, {}}
+\DeclareGraphicsExtensions{.pdf,.png,.jpg}
+
+% Цвета 
+\usepackage[dvipsnames]{xcolor}
+\usepackage{color}
+%\usepackage{colortbl}
 
@@
 
-\author{ Kreinin M. \\
-	Department of Intelligent Systems\\
-	MIPT\\
+%\date{September 9, 1985}	% Here you can change the date presented in the paper title
+%\date{} 					% Or removing it
+
+\author{Kreinin M. \\
+	Department of Data Science\\
+	Moscow Institute of Physics and Technology\\
 	Moscow, Russia \\
 	\texttt{kreinin.mv@phystech.edu} \\
+	%% examples of more authors
         \And
@@
 	Department of Data Science\\
-	MIPT\\
-	Dolgoprudny, Russia \\
+	Moscow Institute of Physics and Technology\\
+	Moscow, Russia \\
 	\texttt{beznosikov.an@phystech.edu} \\
+	%% \AND
+	%% Coauthor \\
+	%% Affiliation \\
+	%% Address \\
+	%% \texttt{email} \\
+	%% \And
+	%% Coauthor \\
+	%% Affiliation \\
+	%% Address \\
+	%% \texttt{email} \\
+	%% \And
+	%% Coauthor \\
+	%% Affiliation \\
+	%% Address \\
+	%% \texttt{email} \\
 }
-\date{}
 
+% Uncomment to remove the date
+%\date{}
+
+% Uncomment to override  the `A preprint' in the header
+%\renewcommand{\headeright}{Technical Report}
+%\renewcommand{\undertitle}{Technical Report}
 \renewcommand{\shorttitle}{\textit{arXiv} Template}
@@
 %%% $ pdfinfo template.pdf
-\hypersetup{
-pdftitle={A template for the arxiv style},
-pdfsubject={q-bio.NC, q-bio.QM},
-pdfauthor={Kreinin M.},
-pdfkeywords={First keyword, Second keyword, More},
-}
 
@@
 \begin{abstract}
-	This paper examines the convergence rate of adaptive gradient methods when a regularization function is added to the target function.
-This is an area of research, since many machine learning problems use the heuristic, heuristic regularization, and we investigate the theoretical and practical convergence of adaptive gradient methods.
+This paper investigates the convergence behavior of optimization methods that utilize weight decay regularization, specifically focusing on popular variants such as AdamW.
+We explore different alternatives to these method, with the goal of investigating their convergence speed and accuracy.
+Also we conduct experiments on benchmark datasets and models in order to compare them on practice.
+Overall, our study provides insights into the design of regularization techniques methods with preconditioning.
 \end{abstract}
 
-\keywords{Adam \and OASIS \and Regularization \and ADAHessian \and Weight Decay}
+\keywords{Adam \and AdamW \and OASIS \and Regularization \and Weight Decay \and Optimization}
 
 \section{Introduction}
+
 In machine learning we consider unconstrained optimization problem
 \begin{equation}
-	\min_{w \in \mathbb{R}^d} f(w)
+    \label{eq:general}
+	\min_{w \in \mathbb{R}^d} f(w).
 \end{equation}
-Problems of the form (1) cover a plethora of applications, including empirical risk minimization,
+Problems of the form \eqref{eq:general} cover a plethora of applications, including empirical risk minimization \citep{chapelle2000vicinal},
 deep learning \citep{lecun2015deep}, and supervised learning \citep{cunningham2008supervised} tasks such as regularized least squares \citep{rifkin2007notes} or logistic regression \citep{shalev2014understanding}.
-This minimization problem can be difficult to solve, particularly when the number of training
-samples n, or problem dimension d, is large, or if the problem is nonconvex.
 
-Second order preconditioners methods are methods when instead of calculate true hessian of our function for newton method \citep{dennis1977quasi}, some heuristics is used to calculate pseudo-hessian.
-There are second order preconditioners methods for solving this problem, such as Adam \citep{kingma2014adam} , OASIS \citep{goldberg2011oasis}, AdaHessian \citep{yao2021adahessian}.
+The classic base method for solving the optimization problem is gradient descent, but this minimization problem can be difficult to solve, particularly when the number of training samples, or problem dimension, is large.
+In such cases, evaluating the full gradient on every iteration in the context of gradient descent becomes prohibitively expensive, especially considering that gradient descent often requires numerous iterations to converge.
+In modern machine learning especially large problems represent the greatest interest.
+For such cases stochastic gradient descent \citep{robbins1951stochastic} became popular solution.
+Despite its simplicity, it proved itself to be an efficient and effective optimization method.
+For a long time first-ordered methods were most popular approach of solving optimization problems.
 
-Throughout this work we assume that each f $:\mathbb{R}^d \rightarrow \mathbb{R}$ is twice differentiable and also L-smooth. This is formalized in the following assumption.
+Other way of solving the problem are methods with adaptive gradient \citep{hazan2007adaptive}. These methods posses several superiority over first-ordered methods.
+Firstly, they have bigger potential of distributed solving, because first ordered methods spend majority of time on "communication".
+Secondly, they are less sensitive to the choice of hyperparameters up to the point that hyperparameters can be set equal to one.
+Lastly, this methods often simply show faster convergence on modern large optimization problems, especially this methods became applicable in neural networks solving \citep{kingma2014adam}.
+Nowadays it is known that preconditioning methods often outperform other methods on modern large optimization problems \citep{goldberg2011oasis, kingma2014adam, zhang2018three, yao2021adahessian}.
 
-\begin{assumption}{1}{Convex}
-	The function f is convex, i.e. $\forall w, w' \in \mathbb{R}^d$
+Preconditioning methods refer to techniques that involve scaling the gradient of a problem by a specific matrix $D_t$, which enables the gradient to take into account the geometry of the problem.
+In the traditional case $D_t = (\nabla^2 f(w))^{-1}$, which corresponds Newton's method, however hessian is difficult to calculate and even more difficult to reverse, because of that some heuristics are used to replace the reversed hessian \citep{dennis1977quasi}.
+In OASIS \citep{jahani2021doubly} or AdaHessian \citep{yao2021adahessian} hessian is assumed to have diagonal dominance.
+In Adam \citep{kingma2014adam} gradient is simply normalized.
+This heuristics were proved to be effective.
+Generally, the step of preconditioned algorithms can be expressed as
 \begin{equation}
-		f(w) \geq f(w') + \langle \nabla F(w'), w-w' \rangle
+    w_t = w_{t-1} - \eta \cdot D_t^{-1} g_t,
 \end{equation}
-\end{assumption}
+where $\eta$ is a learning rate, $D_t$ is a preconditioning matrix, obtained through different heuristics, and $g_t$ is an unbiased stochastic gradient, i.e. $\mathbb{E}[g_t] = \nabla f(w)$.
 
-\begin{assumption}{2}{L-smoothness}
-	The gradients of F are L-Lipschitz continuous $\forall w \in \mathbb{R}^d$, i.e. there exists a constant $L > 0$ such that $\forall w, w' \in \mathbb{R}^d$,
-	\begin{equation*}
-		f(w) \leq f(w') + \langle \nabla f(w'), w-w' \rangle + \frac{L}{2} ||w - w'||^2
-	\end{equation*}
-\end{assumption}
+We do not prescribe the exact method for obtaining $g_t$.
+In large-scale problems, stochastic gradient descent is a more efficient approach since computing the full gradient is prohibitively expensive.
+While computing the Hessian is considerably more costly, so there exist various techniques for computing the preconditioning matrix $D_t$, and we delegate the specific choice of the preconditioning approach to the authors of individual methods.
 
-\begin{assumption}{3}{Twice differentiable}
-	The function f is twice continuously differentiable.
-\end{assumption}
+Despite the various advantages offered by preconditioning methods, they are prone to overfitting.
+As a result, preconditioning methods in practice are almost always utilized with various methods to combat overfitting, with regularization being the primary such method employed.
+Regularization is a powerful technique in machine learning that aims to prevent overfitting by adding additional constraints to the model.
+It has been widely applied to various machine learning problems, including image classification \citep{zhu2017learning}, speech recognition \citep{zhou2017improved}, and natural language processing \citep{wu2022stgn}, and has shown its effectiveness in improving the generalization capability of neural networks \citep{girosi1995regularization}.
 
-\begin{assumption}{4}{$\mu$ - strongly convex}
-	The function f is $\mu$-strongly convex, i.e., there exists a constant $\mu > 0$ such that $\forall w, w' \in \mathbb{R}^d$
-	\begin{equation*}
-		f(w) \geq f(w') + \langle f(w'), w-w' \rangle +\frac{\mu}{2} ||w - w'||^2
-	\end{equation*}
+In methods with preconditioning appears to be several ways to include regularization.
+We can include regularizer $r$ in $g_t$ calculation so it will be taken into consideration while calculating $D_t$. This method is equal to considering optimization problem 
+\begin{equation}
+	\min_{w \in \mathbb{R}^d} f(w) + r(w).
+\end{equation}
+Or we can include regularizer only on last step, decreasing norm of $w$ \citep{loshchilov2017decoupled}.
+This way of regularization is called weight decay and surprisingly turns out to be more efficient in practical problems.
+There are few other ways of considering regularizer which will be discussed further in the paper.
 
-\end{assumption}
+In general, our paper provides insight into comparison of different consideration ways of regularization is methods with preconditioning. Here, we provide a brief summary of our main contributions:
 
-\section{Problem statement}
-We want to investigate the convergence speed of the AdamW method and the newly proposed MyAdamW method in machine learning problems, and we also plan to prove the convergence of these methods and investigate the obtained solution.
+\begin{itemize}
+    \item \textbf{Proof of preconditioned methods with weight decay convergence.}  We derive convergence guarantees for preconditioned methods considering assumptions of smoothness, strongly convex and PL-condition.
 
-We consider the unconstrained optimization problem
-\begin{equation*}
-	\min_{w \in \mathbb{R}^d} f(w)
-\end{equation*}
+    \item \textbf{Research of the loss function.} Comparison of accuracy and loss function for AdamW and AdamL2. As a result we see that AdamW asymptotically converges to a non-zero value.
 
-But we can add regulirazation $r(w)$ -- regularization, and solve the unconstrained optimization problem.
-\begin{equation*}
-	\min_{w \in \mathbb{R}^d} F(w) = f(w) + r(w)
-\end{equation*}
+    \item \textbf{Competitive numerical results.} We investigate the empirical performance of Adam's variation including new one on a variety of standard machine learning tasks, including logistic regression.
+\end{itemize}
 
-In the convergence algorithm that we study, we will investigate algorithms of the following two kinds.
-In the first one, the regularization function is taken out separately in the recalculation of model weights, and in the second one, the function is dominated by the inverse "hessian".
+\section{Regularizer consideration}
+
+\if 0
+\subsection{General preconditioning algorithm}
+
+To begin with, we present the general formulation of preconditioned algorithms in \hyperref[alg:precond]{Algorithm 1}, and the general formulation of first-order algorithms in \hyperref[alg:first]{Algorithm 2}.
+As mentioned briefly earlier, the key distinction of preconditioned methods is the application of the preconditioning matrix $D_t$ to scale the gradient, taking into account second-order information.
+
+\begin{minipage}{0.47\textwidth}
+    \begin{algorithm}[H]
+        \caption{Method with preconditioning}
+        \label{alg:precondgen}
+
+        \begin{algorithmic}
+                \Require{learning rate $\eta$, target function $f$}
+
+                \While {$w$ not converged}
+                \State $t = t+1$
+                \State $g_t \gets$ stochastic gradient
+                \State $D_t \gets$ preconditioning matrix
+                \State $w_t \gets w_{t-1} - \eta \cdot D_t^{-1} g_t$
+                \EndWhile
+        \end{algorithmic}
+    \end{algorithm}
+\end{minipage}
+\hfill
+\begin{minipage}{0.47\textwidth}
+    \begin{algorithm}[H]
+        \caption{First-ordered algorithm}
+        \label{alg:first}
+        \begin{algorithmic}
+                \Require{learning rate $\eta$, target function $f$}
+
+                \While {$w$ not converged}
+                \State $t = t+1$
+                \State $g_t \gets$ stochastic gradient
+                \State $w_t \gets w_{t-1} - \eta \cdot g_t$
+                \EndWhile
+        \end{algorithmic}
+    \end{algorithm}
+\end{minipage}
+
+We do not prescribe the exact method for obtaining $g_t$.
+In large-scale problems, stochastic gradient descent is a more efficient approach since computing the full gradient is prohibitively expensive.
+While computing the Hessian is considerably more costly, so there exist various techniques for computing the preconditioning matrix $D_t$, and we delegate the specific choice of the preconditioning approach to the authors of individual methods.
+
+\subsection{Three ways of regularizer consideration}
+
+\fi
+
+In preconditioned methods, there exist several techniques for incorporating regularization into the optimization process.
+In this study, we consider three different approaches, which are illustrated in \hyperref[alg:precond]{Algorithm 1} using different colors.
+In general, these methods can be characterized by the stage in which the regularization term is incorporated into the optimization process.
 
 \begin{algorithm}[H]
-	\caption{Based algorithm}\label{alg:Based}
-	$w_0, D_0, \eta_0$
-	\begin{algorithmic}
-		\For{$k = 1, 2, ...$}
-		\State $D_k$ - update by using information of $f(w)$
-		\State $\eta_k$ - update
-		\State Set $w_{k+1} = w_k - \eta_k D_k^{-1} \nabla f(w_k) - \eta \nabla r(w)$ 
-		\State or like that
-		\State Set $w_{k+1} = w_k - \eta_k D_k^{-1} (\nabla f(w_k) + \nabla r(w))$
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
-\section{Experiment}
-% Мы проведем эксперимент, в котором сравним Adam с добавленной L2 регуляризацией с AdamW, при различных learning rate и decoupled weight, также мы сравним его с измененным алгоритмом AdamW, где регуляризатор занесен под гессиан, также мы сравним его при условии, что теперь минимальное собственное число гессиана, это не epsilon, а гиперпараметр decoupled weight.Проведем те же эксперименты со SGD и L2 регуляризацией и SGD с decoupled weitght при тех же параметрах.
-Все эксперименты будут проводиться на батчах размера 128, на сетке ResNet18, в 200 эпох.
-Всё это будет реализовано с помощью библиотеки PyTorch на dataset CIFAR10.
-
-We will conduct an experiment in which we compare Adam with added L2 regularization with AdamW, at different learning rate and decoupled weight, also we will compare it with the modified AdamW algorithm where the regularizer is put under the hessian, also we will compare it under the condition that now the minimal eigenvalue of hessian is not epsilon, but decoupled weight hyperparameter.We will conduct the same experiments with SGD and L2 regularization and SGD with decoupled weitght at the same parameters.
-All experiments will be performed on batches of size 128, on a ResNet18 grid of 200 epochs.
-All this will be implemented using the PyTorch library on dataset CIFAR10.
-
-\section{Theory}
-To proof this algorigthm we use simplified form of AdamW algorithm
-\begin{algorithm}[H]
-\caption{AdamW}\label{alg:AdamW}
+    \caption{Different ways of regularization}
+    \label{alg:precond}
 
     \begin{algorithmic}
-    \Require{$r, \varepsilon, f$}    
+            \Require{$\eta, f$}
+
             \While {$w$ not converged}
             \State $t = t+1$
-        \State $D_t = \text{diag}(|\nabla f(w_t)|_i)$
-        \State $w_t = w_{t-1} - \eta \cdot \nabla f(w_t) D_t^{-1}  -\lambda \nabla r(w_t)$ 
+            \State $g_t \gets$ stochastic gradient
+            \State $\textcolor{blue}{g_t \gets g_t + \nabla r(w_t)}$ \hfill \textcolor{blue}{standart regularization}
+            \State $D_t \gets$ preconditioning matrix
+            \State $w_t \gets w_{t-1} - \eta \cdot D_t^{-1} \left(g_t +\textcolor{orange}{\nabla r(w_t)} \right) \textcolor{red}{ - \eta \cdot \nabla r(w_t)}$ \hfill \textcolor{orange}{hessian weight decay}, \textcolor{red}{weight decay}
             \EndWhile
@@
 
+To be more specific, the first regularization technique illustrated in \textcolor{blue}{blue} involves simply adding the regularization term to the objective function.
+This regularizer is included in the pseudo-gradient and factored into the calculation of $D_t$, and can be viewed as solving the following optimization problem:
+\begin{equation*}
+ \min_{w \in \mathbb{R}^d} F(w) = f(w) + r(w),
+\end{equation*}
+where $f(w)$ is the objective function and $r(w)$ is the regularization term. In essence, this approach involves applying the basic preconditioning method to the function $F$.
+
+The second regularization technique, shown in \textcolor{orange}{orange}, is a novel approach.
+Here, the regularization term is added before applying $D_t$, without affecting its computation.
+
+The last regularization approach we consider is known as weight decay, illustrated by the color \textcolor{red}{red} in the \hyperref[alg:precond]{general scheme}.
+This method only incorporates the regularizer during the algorithmic step, avoiding interference of regularization with the preconditioning stage.
+
+Overall, it is important to carefully consider the impact of regularization when designing optimization algorithms, and we hope that our investigation of this techniques will prove useful to researchers in the field.
+
+In our paper we mainly focus on weight decay regularization.
+Though this technique is simpler than the others we consider, it can be quite effective in many cases.
+
+\section{Weight decay regularization}
+
+The most common regularization technique is $\ell_2$ regularization, defined as $r(w_t) = \frac{\lambda}{2} ||w_t||^2$, which yields $\nabla r (w_t) = \lambda \cdot w_t$.
+In this case, the weight decay regularization achieves its name.
+It only serves to reduce the norm of the weight vector, through the subtraction of $\eta \cdot w_t$ in the final step.
+
+However in our theoretical evaluations we use regularizer in general form.
+Thus, algorithmic step that we consider is 
+\begin{equation}
+w_{t+1} = w_t - \eta \cdot D_t^{-1} \nabla f(w_t) - \eta \cdot \nabla r(w_t),
+\end{equation}
+where $D_t$ is a preconditioning matrix, $\eta$ is a learning rate, $f$ is a target function and $r$ is a regularizer.
+
+\subsection{Convergence speed of preconditioning methods}
+
+We set ourselves a goal to estimate a convergence speed of methods with preconditioning with weight decay regularization.
+Although step of methods with weight decay seems simple, it can be viewed in a rather unexpected way. We can put $D_t^{-1}$ out of brackets which gives
+\begin{equation}
+w_{t+1} = w_t - \eta \cdot D_t^{-1} (\nabla f(w_t) + D_t \nabla r(w_t)).
+\end{equation}
+That suggests the need to introduce a variable $\tilde{r}$ such that $\nabla \tilde{r}(w_t) = D_t \nabla r(w_t)$ and new target function $\tilde{F} = f + \tilde{r}$.
+New regularizer $\tilde{r}$ becomes adaptive, because both $r$ and $D_t$ depends on weight vector $w_t$.
+
+The convergence speed is typically measured in terms of the number of iterations required to reach a certain level of error.
+To obtain estimates on the number of iterations required to converge to a given error, we must impose certain assumptions on the function.
+
+Throughout this work we assume that each f $:\mathbb{R}^d \rightarrow \mathbb{R}$ is convex, twice differentiable and L-smooth.
+Additionally we imply a PL-condition to make another evaluation concerning speed of convergence.
+This is formalized in the following assumptions.
+
+\begin{assumption}{1}{Convexity}
+	The function f is convex, i.e. $\forall y, x \in \mathbb{R}^d$
+	\begin{equation*}
+		f(y) \geq f(x) + \langle \nabla f(x), y-x \rangle
+	\end{equation*}
+        \label{ass:convex}
+\end{assumption}
+
+\begin{assumption}{2}{PL--condition}
+	There exists $\mu > 0$, such that $||\nabla f(w) || \geq 2 \mu (f(w) - f^*)$, $\forall w \in \mathbb{R}^d$
+        \label{ass:plcondition}
+\end{assumption}
+
+\begin{assumption}{3}{L-l-smoothness}
+	The gradients of F are L-Lipschitz continuous $\forall w \in \mathbb{R}^d$, i.e. there exists a constant $L > 0$ such that $\forall x, y \in \mathbb{R}^d$,
+	\begin{equation*}
+		f(x) \leq f(y) + \langle \nabla f(y), x-y \rangle + \frac{L}{2} ||x - y||^2
+	\end{equation*}
+    \label{ass:Lsmoothness}
+
+    The gradient of r is l-Lipschitz continuous $\forall w \in \mathbb{R}^d$, i.e. there exists a constant $l > 0$ such that $\forall x, y \in \mathbb{R}^d$,
+	\begin{equation*}
+		r(x) \leq r(y) + \langle \nabla r(y), x-y \rangle + \frac{l}{2} ||x - y||^2
+	\end{equation*}
+        \label{ass:lsmoothness}
+\end{assumption}
+
+Also we must introduce restrictions on preconditioner $D_t$
+\begin{equation}
+\alpha I \preccurlyeq D_t \preccurlyeq \Gamma I \Leftrightarrow \frac{I}{\alpha} \preccurlyeq D_t^{-1} \preccurlyeq \frac{I}{\Gamma}
+\end{equation}
+
+Using introduced assumptions we prooved convergence of methods with preconditioning with weight decay regularization in general form.
+Our results are framed in \hyperref[theor:1]{Theorem 1} and \hyperref[theor:2]{Theorem 2}
+
 \begin{theorem}
-
-Suppose the Assumption 1, 2, 5 and let $\varepsilon > 0$ and let the step-size satisfy
+Suppose the Assumption \hyperref[ass:convex]{1}, \hyperref[ass:Lsmoothness]{2} hold, let $\varepsilon > 0$ and let the step-size satisfy
 \begin{equation*}
@@
 \end{equation*}
-Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem (link here to problem 1) can be bounded by
+Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem \eqref{eq:general} can be bounded by
+\begin{equation*}
+      T = \mathcal{O}\left( \frac{2\Delta_0 \Gamma \alpha } {(2\alpha - \tilde{L}\eta) \eta \varepsilon} \right)
+\end{equation*}
+\label{theor:1}
+\end{theorem}
+
+\begin{theorem}
+    Suppose the Assumption \hyperref[ass:convex]{1}, \hyperref[ass:Lsmoothness]{2}, \hyperref[ass:plcondition]{3} hold, let $\varepsilon > 0$ and let the step-size satisfy
+    \begin{equation*}
+        \eta \leq \frac{2 \alpha}{\tilde{L}}
+    \end{equation*}
+    Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem \eqref{eq:general} can be bounded by
+    \begin{equation*}
+        T =  \mathcal{O}\left( \frac{\ln \frac{\Delta_0}{\epsilon}}{2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha})} \right)
+    \end{equation*}
+    \label{theor:2}
+\end{theorem}
+
+\subsection{Convergence trajectory of preconditioning methods}
+
+ In the previous subsection we have proved convergence of preconditioned methods, however we have pointed out above that methods with weight decay does not converge to the initial optimized function $F = f + r$, but rather to a new function $\tilde{F} = f + \tilde{r}$.
+
+We will consider two algorithms OASIS and Adam, and its variations. Their main difference is in the calculation of the pseudo hessian.
+In Adam, the Hessian is a diagonal matrix consisting of squares of derivatives, in OASIS we have a stochastic Hessian, which is calculated through a random variable from the Randemacher distribution.
+
+We framed three methods of regularization for Adam and OASIS in \hyperref[alg:genAdam]{Algorithm 2} and \hyperref[alg:OASIS]{Algorithm 3} respectively.
+Results of our computational experiments are framed in \hyperref[fig:adams_error]{Figure 1} and \hyperref[fig:oasis_error]{Figure 2}.
+In can be seen that methods with weight decay converges only by special criterion $\nabla f + D_t \nabla r$.
+
+\begin{algorithm}[h]
+
+            \caption{Adam}\label{alg:genAdam}
+
+            \begin{algorithmic}
+            \small{
+            \Require{$\eta, \beta_1, \beta_2, \epsilon, f, r$}
+            %\State $m_0 = 0$ -- 1-st moment vector
+            %\State$v_0 = 0$ -- 2-nd moment vector
+            \While {$\theta$ not converged}
+            \State $t = t+1$
+            \State $g_t = \nabla f(w_{t-1}) + $ \textcolor{blue}{$\nabla r(w_{t-1})$}\hfill \textcolor{blue}{AdamL2}
+            \State $m_t = \beta_1 \cdot m_{t-1} + (1 - \beta_1) \cdot g_t$
+            \State $v_t = \beta_2 \cdot v_{t-1} + (1 - \beta_2) \cdot g_t^2$
+            \State $\hat{m_t} = \frac{m_t}{1-\beta_1^t} +$ \textcolor{orange}{$\nabla r(w_{t-1})$} \hfill \textcolor{orange}{AdamWH}
+            \State $\hat{v_t} = \frac{v_t}{1-\beta_2^t}$ 
+            \State $w_t = w_{t-1} - \eta \cdot \frac{\hat{m_t}}{\sqrt{v_t} + \epsilon} - $ \textcolor{red}{$\eta \nabla r(w_{t-1})$ } \hfill \textcolor{red}{AdamW}
+            \EndWhile
+            }
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[h]
+\caption{OASIS}\label{alg:OASIS}
+\begin{algorithmic}
+    \Require{$w_0, \eta_0, D_0, \theta_0 = + \infty$}    
+    \State $w_1 = w_0 - \eta \hat{D_0}^{-1} \nabla f(w_0)$
+
+    \For{$k = 1, 2, ...$}
+    \State $g_k = \nabla f(w_k) +$ \textcolor{blue}{$\nabla r(w_{t-1})$}\hfill \textcolor{blue}{OASISL2} 
+    \State $D_k = \beta D_{k-1} + (1-\beta_2) \cdot diag\left( z_k \odot \nabla^2 \left(f(w_k) + \textcolor{orange}{r(w_k)} \right) z_k \right)$ \hfill \textcolor{orange}{OASISWH}
+    \State $(\hat{D_k})_{ii} = max \{|D_k|_{i, i} ; \alpha \}$, $\forall i = \overline{1, d}$
+    \State $\eta_k = min \{ \sqrt{1 + \theta_{k-1}} \cdot \eta_{k-1}; \frac{||w_k - w_{k-1}||_{\hat{D_k}}}{2 ||\nabla f(w_k) - \nabla f(w_{k-1}) ||_{\hat{D_k}}^* } \}$
+    \State $w_{k+1} = w_k - \eta_k g_k D_k^{-1}- $ \textcolor{red}{$\eta \nabla r(w_{t-1})$ } \hfill \textcolor{red}{OASISW} 
+    \State $\theta_k = \frac{\eta_k}{\eta_{k-1}}$
+    \EndFor
+
+\end{algorithmic}
+\end{algorithm}
+
+Thus, method converges to another solution,
+
+\begin{minipage}{0.5\textwidth}
+\begin{figure}[H]
+\centering
+    \includegraphics[width=\textwidth]{pictures/mushrooms/adams_error.png}
+    \caption{Adam on dataset mushrooms}
+        \label{fig:adams_error}
+\end{figure}
+\end{minipage}
+\hfill
+\begin{minipage}{0.5\textwidth}
+\begin{figure}[H]
+\centering
+    \includegraphics[width=\textwidth]{pictures/mushrooms/oasis_error.png}
+    \caption{OASIS on dataset mushrooms}
+        \label{fig:oasis_error}
+\end{figure}
+\label{fig:error}
+\end{minipage}
+
+\begin{figure}[H]
+\centering
+    \includegraphics[width=0.9\textwidth]{pictures/mushrooms/main_adam.png}
+    \caption{Dataset: mushrooms}
+
+        \label{fig:main_mushrooms_adam}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+    \includegraphics[width=0.9\textwidth]{pictures/mushrooms/main_mushrooms.png}
+    \caption{Dataset: mushrooms}
+
+        \label{fig:main_mushrooms}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+    \includegraphics[width=0.9\textwidth]{pictures/wine/main_wine.png}
+    \caption{Dataset: wine}
+
+        \label{fig:main_wine}
+\end{figure}
+
+\subsection{Computational experiment}
+
+\bibliographystyle{unsrtnat}
+\bibliography{refs}
+
+\newpage
+\section{Appendix}
+\begin{theorem}
+Suppose the Assumption \hyperref[ass:convex]{1}, \hyperref[ass:Lsmoothness]{2} and let $\varepsilon > 0$ and let the step-size satisfy
+\begin{equation*}
+    \eta < \frac{2 \alpha}{L + l \cdot \alpha} 
+\end{equation*}
+Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem \eqref{eq:general} can be bounded by
 \begin{equation*}
@@
 
-Let's write first assumption for step t and $t+1$:
+Let's write \ref{ass:convex} for step t and $t+1$:
 
 \begin{equation*}
-    f(w_{t+1}) \leq f(w_t) + \langle \nabla f(w_t), w_{t+1} - w_t \rangle + \frac{L}{2}||w_{t+1} - w_t ||^2
+    f(w_{t+1}) \leq f(w_t) + \langle \nabla f(w_t), w_{t+1} - w_t \rangle + \frac{L}{2}||w_{t+1} - w_t ||^2,
 \end{equation*}
@@
 \begin{equation*}
-w_{t+1} - w_t = -\eta D_t^{-1} \nabla f(w_t) - \eta \nabla r(w_t)    
+w_{t+1} - w_t = -\eta D_t^{-1} \nabla f(w_t) - \eta \nabla r(w_t),
 \end{equation*}
 
-and
+from the previous expression , we express the gradient of the function
 
 \begin{equation*}
-\nabla f(w_t) = \frac{1}{\eta} D^t(w_t - w_{t+1}) - D^t \nabla r(w_t)
+\nabla f(w_t) = \frac{1}{\eta} D^t(w_t - w_{t+1}) - D^t \nabla r(w_t),
 \end{equation*}
 
-Okay, now let's replace $\nabla f(w_t)$ and $I \leq \frac{D_t}{\alpha}$
+replace $\nabla f(w_t)$ and by definition of matrix $D_t$, $I \leq \frac{D_t}{\alpha}$
 \begin{equation*}
-    f(w_{t+1}) \leq f(w_t) + \langle \frac{1}{\eta}D_t(w_t - w_{t+1}) - D_t\nabla r(w_t), w_{t+1} - w_t \rangle + \frac{L}{2 \alpha} ||w_{t+1} - w_t||_{D_t}^2
+    f(w_{t+1}) \leq f(w_t) + \langle \frac{1}{\eta}D_t(w_t - w_{t+1}) - D_t\nabla r(w_t), w_{t+1} - w_t \rangle + \frac{L}{2 \alpha} ||w_{t+1} - w_t||_{D_t}^2,
 \end{equation*}
 
+now let's bring it together
 \begin{equation*}
-    f(w_{t+1}) \leq f(w_t) + \left(\frac{L}{2 \alpha} - \frac{1}{\eta} \right) ||w_{t+1} - w_t||_{D_t}^2 - \langle D_t \nabla r(w_t), w_{t+1} - w_t \rangle
+    f(w_{t+1}) \leq f(w_t) + \left(\frac{L}{2 \alpha} - \frac{1}{\eta} \right) ||w_{t+1} - w_t||_{D_t}^2 - \langle D_t \nabla r(w_t), w_{t+1} - w_t \rangle,
 \end{equation*}
 
-Lets define new variable $\tilde{r} : \nabla \tilde{r} = D_t \nabla r(w_t)$. Then rewrite step using the variable and 5-th assumption.
+define new regularization function $\tilde{r} : \nabla \tilde{r} = D_t \nabla r(w_t)$.
+
+then rewrite step using the variable and assumption \ref{ass:lsmoothness}
 \begin{equation*}
-    \tilde{r}(w_{t+1}) \leq \tilde{r}(w_t) + \langle \tilde{r}(w_t), w_{t+1} - w_t \rangle + \frac{l}{2} (w_{t+1} - w_t)^T D_t (w_{t+1} - w_t)
+    \tilde{r}(w_{t+1}) \leq \tilde{r}(w_t) + \langle \tilde{r}(w_t), w_{t+1} - w_t \rangle + \frac{l}{2} (w_{t+1} - w_t)^T D_t (w_{t+1} - w_t),
 \end{equation*}
 
+let's replace the old regularization function with a new one
+
 \begin{equation*}
-    f(w_{t+1}) \leq f(w_t) + \left( \frac{L}{2\alpha} - \frac{1}{\eta} \right) ||w_{t+1} - w_t||_{D_t}^2 + \tilde{r}(w_t) - \tilde{r}(w_{t+1}) + \frac{l}{2}||w_{t+1}-w_t||_{D_t}^2
+    f(w_{t+1}) \leq f(w_t) + \left( \frac{L}{2\alpha} - \frac{1}{\eta} \right) ||w_{t+1} - w_t||_{D_t}^2 + \tilde{r}(w_t) - \tilde{r}(w_{t+1}) + \frac{l}{2}||w_{t+1}-w_t||_{D_t}^2,
 \end{equation*}
 
+now let's define a new loss function
 $\tilde{F}(w) = f(w) + \tilde{r}(w)$, $F(w) = f(w) + r(w)$, ($\tilde{L}=L + l \alpha$), we get:
 
+let's rewrite our inequality in new notation
+
 \begin{equation*}
-    \tilde{F}(w_{t+1}) \leq \tilde{F}(w_t) + \left( \frac{\tilde{L}}{2\alpha} - \frac{1}{\eta}  \right) ||w_{t+1} - w_t||_{D_t}^2
+    \tilde{F}(w_{t+1}) \leq \tilde{F}(w_t) + \left( \frac{\tilde{L}}{2\alpha} - \frac{1}{\eta}  \right) ||w_{t+1} - w_t||_{D_t}^2,
 \end{equation*}
 
+now we select the step in such a way that $ \frac{\tilde{L}}{2\alpha} - \frac{1}{\eta} < 0$,  $\eta < \frac{2 \alpha}{\tilde{L}}$
 \begin{equation*}
-    \left(\frac{1}{\eta} - \frac{\tilde{L}}{2\alpha}   \right) ||w_{t+1} - w_t||_{D_t}^2 \leq \tilde{F}(w_t) - \tilde{F}(w_{t+1})
+    \left(\frac{1}{\eta} - \frac{\tilde{L}}{2\alpha}   \right) ||w_{t+1} - w_t||_{D_t}^2 \leq \tilde{F}(w_t) - \tilde{F}(w_{t+1}),
 \end{equation*}
 
+let's sum up our inequalities and evaluate the left part from below
 \begin{equation*}
-    \frac{\eta^2  (T+1)}{\Gamma}\left(\frac{1}{\eta} - \frac{\tilde{L}}{2\alpha}   \right)\cdot\min_{k = 0, T} ||\nabla f(w_t) + \nabla \tilde{r}(w_t)||^2 \leq \frac{\eta^2}{\Gamma}\left(\frac{1}{\eta} - \frac{\tilde{L}}{2\alpha}   \right)\cdot\sum\limits_{t = 0}^T ||\nabla f(w_t) + \nabla \tilde{r}(w_t)||^2 \leq \tilde{F}(w_0) - \tilde{F}(w_*)
+    \frac{\eta^2  (T+1)}{\Gamma}\left(\frac{1}{\eta} - \frac{\tilde{L}}{2\alpha}   \right)\cdot\min_{k = 0, T} ||\nabla f(w_t) + \nabla \tilde{r}(w_t)||^2 \leq \frac{\eta^2}{\Gamma}\left(\frac{1}{\eta} - \frac{\tilde{L}}{2\alpha}   \right)\cdot\sum\limits_{t = 0}^T ||\nabla f(w_t) + \nabla \tilde{r}(w_t)||^2 \leq \tilde{F}(w_0) - \tilde{F}(w_*),
 \end{equation*}
+
+moving everything to the right we get the following estimate
 
@@
 
-Then:
+we get an estimate for the number of steps required for a given accuracy
 \begin{equation*}
@@
 \begin{theorem}
-    Suppose the Assumption 1, 2, 4, 5 and let $\varepsilon > 0$ and let the step-size satisfy
+    Suppose the Assumption \hyperref[ass:convex]{1}, \hyperref[ass:Lsmoothness]{2}, \hyperref[ass:plcondition]{3} and let $\varepsilon > 0$ and let the step-size satisfy
     \begin{equation*}
@@
     \end{equation*}
-    Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem (link here to problem 1) can be bounded by
+    Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem \eqref{eq:general} can be bounded by
     \begin{equation*}
@@
 \begin{proof}
+    The proof of this theorem will be similar to the previous one, the main difference is that we impose another assumoption \ref{ass:plcondition} on the original function 
     Assume 
-    \begin{equation}
+    \begin{equation*}
     \nabla \tilde{F} = \nabla f + \nabla \tilde{r}    
-    \end{equation}
+    \end{equation*}
 
-    \begin{equation}
+    \begin{equation*}
     L + ||D_t||l = \tilde{L}        
-    \end{equation}
+    \end{equation*}
+    rewrite step in terms of new function
     \begin{equation*}
-    w_{t+1} - w_t = -\eta D_t^{-1} \nabla r(w_t) - \eta \nabla r(w_t) = -\eta D_t^{-1} (\nabla f + \nabla \tilde{r})(w_t) = -\eta D_t^{-1} \nabla \tilde{F}(w_t)    
+    w_{t+1} - w_t = -\eta D_t^{-1} \nabla r(w_t) - \eta \nabla r(w_t) = -\eta D_t^{-1} (\nabla f + \nabla \tilde{r})(w_t) = -\eta D_t^{-1} \nabla \tilde{F}(w_t),
     \end{equation*}
@@
     \begin{equation*}
-        \tilde{F}(w_{t+1}) - \tilde{F}(w_t) \leq  \langle \nabla \tilde{F}(w_t), w_{t+1} - w_t \rangle + \frac{\tilde{L}}{2} ||w_{t+1} - w_t||^2
+        \tilde{F}(w_{t+1}) - \tilde{F}(w_t) \leq  \langle \nabla \tilde{F}(w_t), w_{t+1} - w_t \rangle + \frac{\tilde{L}}{2} ||w_{t+1} - w_t||^2,
     \end{equation*}
+    then combine it together and use constraints on the matrix $\alpha \cdot I \preccurlyeq D_t \preccurlyeq \Gamma \cdot I$
+    \begin{eqnarray*}
+&& \        \tilde{F}(w_{t+1}) - \tilde{F}(w_t) \leq - \langle \frac{1}{\eta} D_t(w_{t+1} - w_t), w_{t+1} - w_t \rangle + \frac{\tilde{L}}{2} ||w_{t+1} - w_t||^2 = (\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) ||w_{t+1} - w_t||^2_{D_t} =
+\notag\\& =&
+(\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) ||w_{t+1} - w_t||^2_{D_t} = (\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) ||-\eta D_t^{-1} \nabla \tilde{F}(w_t)||_{D_t}^2  \leq (\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) \eta^2 ||\nabla \tilde{F}(w_t)||^2_{D_t^{-1}},
+\end{eqnarray*}
+
+    Then we use PL-condition \ref{ass:plcondition} for the function $\tilde{F}$:
     \begin{equation*}
-        \tilde{F}(w_{t+1}) - \tilde{F}(w_t) \leq - \langle \frac{1}{\eta} D_t(w_{t+1} - w_t), w_{t+1} - w_t \rangle + \frac{\tilde{L}}{2} ||w_{t+1} - w_t||^2 = (\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) ||w_{t+1} - w_t||^2_{D_t}
-    \end{equation*}
-    \begin{equation*}
-        = (\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) ||w_{t+1} - w_t||^2_{D_t} = (\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) ||-\eta D_t^{-1} \nabla \tilde{F}(w_t)||_{D_t}^2  \leq (\frac{\tilde{L}}{2 \alpha} - \frac{1}{\eta}) \eta^2 ||\nabla \tilde{F}(w_t)||^2_{D_t^{-1}}
-    \end{equation*}
-    Then we use PL-condition for the function $\tilde{F}$:
-    \begin{equation*}
-        ||\nabla \tilde{F}(w_t)||_{D_t^{-1}}^2 \geq 2 \mu (\tilde{F}(w_t) - \tilde{F}^*)
+        ||\nabla \tilde{F}(w_t)||_{D_t^{-1}}^2 \geq 2 \mu (\tilde{F}(w_t) - \tilde{F}^*),
     \end{equation*}
 
+    subtract the exact solution from both parts and apply PL-condition
     \begin{equation*}
-    \tilde{F}(w_{t}) -  F^* \ge \tilde{F}(w_{t+1}) - \tilde{F}^* + (\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}) \eta^2 2 \mu (\tilde{F}(w_t) - \tilde{F}^*) = \left( 1 +  2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}) \right) (\tilde{F}(w_{t+1}) - \tilde{F}^*)
+    \tilde{F}(w_{t}) -  F^* \ge \tilde{F}(w_{t+1}) - \tilde{F}^* + (\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}) \eta^2 2 \mu (\tilde{F}(w_t) - \tilde{F}^*) = \left( 1 +  2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}) \right) (\tilde{F}(w_{t+1}) - \tilde{F}^*),
     \end{equation*}
 
+    we apply the expression for each step, $\Delta_0 = \tilde{F}(w_0) - \tilde{F}(w_{*})$
     \begin{equation*}
-    \epsilon \ge \Delta_0 \left( 1 +  2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}) \right)^{-T} \ge (\tilde{F}(w_{T}) - \tilde{F}^*)        
+    \varepsilon \ge \Delta_0 \left( 1 +  2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}) \right)^{-T} \ge (\tilde{F}(w_{T}) - \tilde{F}^*),     
     \end{equation*}
 
+    we get the necessary number of steps to get together with the error $\varepsilon$
     \begin{equation*}
-    T = \frac{\ln \frac{\Delta_0}{\epsilon}}{\ln(1 + 2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}))} \approx \frac{\ln \frac{\Delta_0}{\epsilon}}{2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha})}
+    T = \frac{\ln \frac{\Delta_0}{\varepsilon}}{\ln(1 + 2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha}))} \approx \frac{\ln \frac{\Delta_0}{\varepsilon}}{2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha})}
     \end{equation*}
-    Then:
+    and finally we get:
     \begin{equation*}
-    T =  \mathcal{O}\left( \frac{\ln \frac{\Delta_0}{\epsilon}}{2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha})} \right)
+    T =  \mathcal{O}\left( \frac{\ln \frac{\Delta_0}{\varepsilon}}{2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha})} \right)
     \end{equation*}
@@
 
-\bibliographystyle{unsrtnat}
-\bibliography{references}
+\subsection{Experiments:}
+\subsubsection{Mushrooms}
+\begin{figure}[h]
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/mushrooms/m_adamw_2000_1.png}}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/mushrooms/m_adamw_2000_2.png}}
+\end{minipage}
+\caption{AdamW on dataset mushrooms}
+
+\label{fig:m_adamw}
+\end{figure}
+
+\begin{figure}[h]
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/mushrooms/m_adamwh_2000_1.png}}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/mushrooms/m_adamwh_2000_2.png}}
+\end{minipage}
+\caption{AdamWH on dataset mushrooms}
+\label{fig:m_adamwh}
+\end{figure}
+
+\begin{figure}[h]
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/mushrooms/m_oasisw_1.png}}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/mushrooms/m_oasisw_2.png}}
+\end{minipage}
+\caption{OASISW on dataset mushrooms}
+\label{fig:m_oasisw}
+\end{figure}
+
+\begin{figure}[h]
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/mushrooms/m_oasiswh_1.png}}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/mushrooms/m_oasiswh_2.png}}
+\end{minipage}
+\caption{OASISWH on dataset mushrooms}
+\label{fig:m_oasiswh}
+\end{figure}
+
+\begin{figure}[H]
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/mushrooms/m_gd_2000.png}}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/mushrooms/m_adaml2_2000.png}}
+\end{minipage}
+\caption{Gradient descent and AdamL2 on dataset mushrooms}
+\label{fig:m_gd_adaml2}
+\end{figure}
+
+%xuy 
+\subsubsection{Wine}
+
+\begin{figure}[H]
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/wine/w_adamw_2000_1.png}}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/wine/w_adamw_2000_2.png}}
+\end{minipage}
+\caption{AdamW on dataset wine}
+
+\label{fig:w_adamw}
+\end{figure}
+
+\begin{figure}[H]
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/wine/w_adamwh_2000_1.png}}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/wine/w_adamwh_2000_2.png}}
+\end{minipage}
+\caption{AdamWH on dataset wine}
+\label{fig:w_adamwh}
+\end{figure}
+
+\begin{figure}[H]
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/wine/w_oasis_2000_1.png}}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/wine/w_oasis_2000_2.png}}
+\end{minipage}
+\caption{OASISW on dataset wine}
+\label{fig:w_oasisw}
+\end{figure}
+
+\begin{figure}[H]
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/wine/w_gd_2000.png}}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.5\linewidth}
+\center{\includegraphics[width=\linewidth]{pictures/wine/w_adaml2_2000.png}}
+\end{minipage}
+\caption{Gradient descent and AdamL2 on dataset wine}
+\label{fig:w_gd_adaml2}
+\end{figure}
 

### 2023-04-22 code/adamwh.py

@@ -1,0 +1,388 @@
+from torch.optim import AdamW
+import math
+import torch
+from torch import Tensor
+from typing import List
+
+class MyAdamW(AdamW):
+    @torch.no_grad()
+    def step(self, closure=None):
+        """Performs a single optimization step.
+
+        Args:
+            closure (Callable, optional): A closure that reevaluates the model
+                and returns the loss.
+        """
+        self._cuda_graph_capture_health_check()
+
+        loss = None
+        if closure is not None:
+            with torch.enable_grad():
+                loss = closure()
+
+        for group in self.param_groups:
+            params_with_grad = []
+            grads = []
+            exp_avgs = []
+            exp_avg_sqs = []
+            max_exp_avg_sqs = []
+            state_steps = []
+            amsgrad = group['amsgrad']
+            beta1, beta2 = group['betas']
+            
+
+            for p in group['params']:
+                if p.grad is None:
+                    continue
+                params_with_grad.append(p)
+                if p.grad.is_sparse:
+                    raise RuntimeError('AdamW does not support sparse gradients')
+                grads.append(p.grad)
+
+                state = self.state[p]
+
+                # State initialization
+                if len(state) == 0:
+                    state['step'] = torch.zeros((1,), dtype=torch.float, device=p.device) \
+                        if self.defaults['capturable'] else torch.tensor(0.)
+                    # Exponential moving average of gradient values
+                    state['exp_avg'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+                    # Exponential moving average of squared gradient values
+                    state['exp_avg_sq'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+                    if amsgrad:
+                        # Maintains max of all exp. moving avg. of sq. grad. values
+                        state['max_exp_avg_sq'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+
+                exp_avgs.append(state['exp_avg'])
+                exp_avg_sqs.append(state['exp_avg_sq'])
+
+                if amsgrad:
+                    max_exp_avg_sqs.append(state['max_exp_avg_sq'])
+
+                state_steps.append(state['step'])
+
+            myadamw(params_with_grad,
+                  grads,
+                  exp_avgs,
[…]

### 2023-04-22 code/lib.py

@@ -7,7 +7,7 @@ from datetime import datetime as dt
 from tqdm import tqdm
 
 class MyLogregression:
-    def __init__(self, fit_intercept=False, eps=5*1e-3,     iter =10 ** 3, batch=False, batch_size=50, decreasing_lr=False, name="GD", lr_func = None, label="None", dependent=False, l2_coef=0, betas = [0.999, 0.99]):
+    def __init__(self, fit_intercept=False, eps=5*1e-6,     iter =10 ** 3, batch=False, batch_size=50, decreasing_lr=False, name="GD", lr_func = None, label="None", dependent=False, l2_coef=0, betas = [0.999, 0.99]):
         self.fit_intercept = fit_intercept
         self._iter         = iter
         self._batch        = batch
@@ -22,7 +22,7 @@ class MyLogregression:
         self._l2_coef      = l2_coef
         self._betas        = betas
         self._grad_function = self.__grad_function
-        if name == "AdamL2" or name == "AdamW":
+        if name == "AdamL2" or name == "AdamW" or name == "OASIS" or name == "AdamWH":
             self._error_criterion = lambda w: np.linalg.norm(self._grad_function(w) + self._l2_coef * w, 2)
         else:
             self._error_criterion = lambda w: np.linalg.norm(self._grad_function(w), 2)
@@ -44,7 +44,7 @@ class MyLogregression:
         for i in range(len(self._y_train)):            
             up = self._y_train[i] * self._X_train[i] * np.exp(-self._y_train[i] * w * self._X_train[i])
             down = n * (1 + np.exp(-self._y_train[i] * w * self._X_train[i]))
-            sum = sum  - up/down
+            sum = sum - up/down
 
         return sum
 
@@ -174,7 +174,7 @@ class MyLogregression:
             self._w = self._w - lr(0) * grad_f(self._w)
             self._w = self._w - lr(0) * m_bias_corr / (np.sqrt(v_bias_corr) + eps) - lr(0) * self._l2_coef * self._w
             
-            self._error_adamw.append(np.linalg.norm(m_bias_corr + self._l2_coef * self._w * v_bias_corr , 2))
+            self._error_adamw.append(np.linalg.norm(m_bias_corr + self._l2_coef * self._w * (np.sqrt(v_bias_corr) + eps), 2))
             self._append_errors(self._w, time_start)
             
             if (self._errors[-1] < self._eps):
[…]

### 2023-04-22 code/main.py

@@ -1,0 +1,192 @@
+'''Train CIFAR10 with PyTorch.'''
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import torch.nn.functional as F
+import torch.backends.cudnn as cudnn
+
+import torchvision
+import torchvision.transforms as transforms
+
+import os
+import argparse
+import sys
+
+from myadam import MyAdamW
+
+from resnet import ResNet18
+
+from tqdm import tqdm
+#from torch.utils import progress_bar
+from torch.utils.tensorboard import SummaryWriter
+
+
+def test(epoch):
+    global best_acc
+    global test_step
+    net.eval()
+    test_loss = 0
+    test_loss_true = 0
+    correct = 0
+    total = 0
+    with torch.no_grad():
+        loop = tqdm(enumerate(testloader), total=len(testloader), leave=False)
+        for batch_idx, (inputs, targets) in loop:
+            test_step += 1
+            inputs, targets = inputs.to(device), targets.to(device)
+            outputs = net(inputs)
+            loss = criterion(outputs, targets)
+
+            test_loss += loss.item()
+            #
+            test_loss_true += loss.item()
+
+            _, predicted = outputs.max(1)
+            total += targets.size(0)
+            correct += predicted.eq(targets).sum().item()
+            
+            writer.add_scalar('Testing loss', test_loss/(batch_idx+1),global_step=test_step)
+            writer.add_scalar('Testing loss true', test_loss_true/(batch_idx+1),global_step=test_step)
+            writer.add_scalar('Testing accuracy', 100.*correct/total, global_step=test_step)
+            
+            loop.set_description(f"{full_name}Epoch (Test)[{epoch}/{num_epoch}]")
+            loop.set_postfix(loss= test_loss/(batch_idx+1), acc=100.*correct/total,correct=correct, total=total)
+
+    # Save checkpoint.
+    acc = 100.*correct/total
+    if acc > best_acc:
+        print('Saving..')
+        state = {
+            'net': net.state_dict(),
+            'acc': acc,
+            'epoch': epoch,
+        }
+        if not os.path.isdir('checkpoint'):
+            os.mkdir('checkpoint')
+        torch.save(state, f'./checkpoint/ckpt.pth')
+        best_acc = acc
+    return test_loss, correct, total, test_loss_true
+
+# Training
+def train(epoch):
+    #print('\nEpoch: %d' % epoch)
+    global train_step
+    net.train()
+    train_loss = 0
+    train_loss_true = 0
+    correct = 0
+    total = 0
[…]

### 2023-04-22 code/myadam.py

@@ -1,387 +1,0 @@
-from torch.optim import AdamW
-import math
-import torch
-from torch import Tensor
-from typing import List
-
-class MyAdamW(AdamW):
-    @torch.no_grad()
-    def step(self, closure=None):
-        """Performs a single optimization step.
-
-        Args:
-            closure (Callable, optional): A closure that reevaluates the model
-                and returns the loss.
-        """
-        self._cuda_graph_capture_health_check()
-
-        loss = None
-        if closure is not None:
-            with torch.enable_grad():
-                loss = closure()
-
-        for group in self.param_groups:
-            params_with_grad = []
-            grads = []
-            exp_avgs = []
-            exp_avg_sqs = []
-            max_exp_avg_sqs = []
-            state_steps = []
-            amsgrad = group['amsgrad']
-            beta1, beta2 = group['betas']
-
-            for p in group['params']:
-                if p.grad is None:
-                    continue
-                params_with_grad.append(p)
-                if p.grad.is_sparse:
-                    raise RuntimeError('AdamW does not support sparse gradients')
-                grads.append(p.grad)
-
-                state = self.state[p]
-
-                # State initialization
-                if len(state) == 0:
-                    state['step'] = torch.zeros((1,), dtype=torch.float, device=p.device) \
-                        if self.defaults['capturable'] else torch.tensor(0.)
-                    # Exponential moving average of gradient values
-                    state['exp_avg'] = torch.zeros_like(p, memory_format=torch.preserve_format)
-                    # Exponential moving average of squared gradient values
-                    state['exp_avg_sq'] = torch.zeros_like(p, memory_format=torch.preserve_format)
-                    if amsgrad:
-                        # Maintains max of all exp. moving avg. of sq. grad. values
-                        state['max_exp_avg_sq'] = torch.zeros_like(p, memory_format=torch.preserve_format)
-
-                exp_avgs.append(state['exp_avg'])
-                exp_avg_sqs.append(state['exp_avg_sq'])
-
-                if amsgrad:
-                    max_exp_avg_sqs.append(state['max_exp_avg_sq'])
-
-                state_steps.append(state['step'])
-
-            myadamw(params_with_grad,
-                  grads,
-                  exp_avgs,
[…]

### 2023-04-22 code/pytorch logreg/s_adamw.py

@@ -1,0 +1,355 @@
+'''Train CIFAR10 with PyTorch.'''
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import torch.nn.functional as F
+import torch.backends.cudnn as cudnn
+
+import torchvision
+import torchvision.transforms as transforms
+
+import os
+import argparse
+import sys
+
+from torch.optim import AdamW
+import math
+import torch
+from torch import Tensor
+from typing import List
+
+class our_AdamW(AdamW):
+    @torch.no_grad()
+    def step(self, closure=None):
+        """Performs a single optimization step.
+
+        Args:
+            closure (Callable, optional): A closure that reevaluates the model
+                and returns the loss.
+        """
+        self._cuda_graph_capture_health_check()
+
+        loss = None
+        if closure is not None:
+            with torch.enable_grad():
+                loss = closure()
+
+        for group in self.param_groups:
+            params_with_grad = []
+            grads = []
+            exp_avgs = []
+            exp_avg_sqs = []
+            max_exp_avg_sqs = []
+            state_steps = []
+            amsgrad = group['amsgrad']
+            beta1, beta2 = group['betas']
+
+            for p in group['params']:
+                if p.grad is None:
+                    continue
+                params_with_grad.append(p)
+                if p.grad.is_sparse:
+                    raise RuntimeError('AdamW does not support sparse gradients')
+                grads.append(p.grad)
+
+                state = self.state[p]
+
+                # State initialization
+                if len(state) == 0:
+                    state['step'] = torch.zeros((1,), dtype=torch.float, device=p.device) \
+                        if self.defaults['capturable'] else torch.tensor(0.)
+                    # Exponential moving average of gradient values
+                    state['exp_avg'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+                    # Exponential moving average of squared gradient values
+                    state['exp_avg_sq'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+                    if amsgrad:
+                        # Maintains max of all exp. moving avg. of sq. grad. values
+                        state['max_exp_avg_sq'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+
+                exp_avgs.append(state['exp_avg'])
[…]

### 2023-04-22 code/pytorch logreg/s_adamwh.py

@@ -1,0 +1,353 @@
+'''Train CIFAR10 with PyTorch.'''
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import torch.nn.functional as F
+import torch.backends.cudnn as cudnn
+
+import torchvision
+import torchvision.transforms as transforms
+
+import os
+import argparse
+import sys
+
+from torch.optim import AdamW
+import math
+import torch
+from torch import Tensor
+from typing import List
+
+class AdamWH(AdamW):
+    @torch.no_grad()
+    def step(self, closure=None):
+        """Performs a single optimization step.
+
+        Args:
+            closure (Callable, optional): A closure that reevaluates the model
+                and returns the loss.
+        """
+        self._cuda_graph_capture_health_check()
+
+        loss = None
+        if closure is not None:
+            with torch.enable_grad():
+                loss = closure()
+
+        for group in self.param_groups:
+            params_with_grad = []
+            grads = []
+            exp_avgs = []
+            exp_avg_sqs = []
+            max_exp_avg_sqs = []
+            state_steps = []
+            amsgrad = group['amsgrad']
+            beta1, beta2 = group['betas']
+
+            for p in group['params']:
+                if p.grad is None:
+                    continue
+                params_with_grad.append(p)
+                if p.grad.is_sparse:
+                    raise RuntimeError('AdamW does not support sparse gradients')
+                grads.append(p.grad)
+
+                state = self.state[p]
+
+                # State initialization
+                if len(state) == 0:
+                    state['step'] = torch.zeros((1,), dtype=torch.float, device=p.device) \
+                        if self.defaults['capturable'] else torch.tensor(0.)
+                    # Exponential moving average of gradient values
+                    state['exp_avg'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+                    # Exponential moving average of squared gradient values
+                    state['exp_avg_sq'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+                    if amsgrad:
+                        # Maintains max of all exp. moving avg. of sq. grad. values
+                        state['max_exp_avg_sq'] = torch.zeros_like(p, memory_format=torch.preserve_format)
+
+                exp_avgs.append(state['exp_avg'])
[…]

### 2023-05-02 paper/main.tex
rewrite paper

@@
 \usepackage{color}   
-%\usepackage{colortbl}
+% Возможность сделать 14-й шрифт
 
@@
 	\texttt{kreinin.mv@phystech.edu} \\
-	%% examples of more authors
 	\And
@@
 	\texttt{beznosikov.an@phystech.edu} \\
-	%% \AND
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-	%% \And
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-	%% \And
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
 }
@@
 % Uncomment to override  the `A preprint' in the header
-%\renewcommand{\headeright}{Technical Report}
+\renewcommand{\headeright}{}
 %\renewcommand{\undertitle}{Technical Report}
-\renewcommand{\shorttitle}{\textit{arXiv} Template}
+%\renewcommand{\shorttitle}{\textit{arXiv} Template}
 
@@
 \begin{abstract}
-This paper investigates the convergence behavior of optimization methods that utilize weight decay regularization, specifically focusing on popular variants such as AdamW.
+This paper investigates the convergence behavior of optimization methods with preconditioning that utilize weight decay regularization, specifically focusing on popular variants such as AdamW and OASIS.
 We explore different alternatives to these method, with the goal of investigating their convergence speed and accuracy.
@@
 There are few other ways of considering regularizer which will be discussed further in the paper.
-
+\if 0
 In general, our paper provides insight into comparison of different consideration ways of regularization is methods with preconditioning. Here, we provide a brief summary of our main contributions:
@@
 \end{itemize}
-
-\section{Regularizer consideration}
-
-\if 0
-\subsection{General preconditioning algorithm}
-
-To begin with, we present the general formulation of preconditioned algorithms in \hyperref[alg:precond]{Algorithm 1}, and the general formulation of first-order algorithms in \hyperref[alg:first]{Algorithm 2}.
-As mentioned briefly earlier, the key distinction of preconditioned methods is the application of the preconditioning matrix $D_t$ to scale the gradient, taking into account second-order information.
-
-\begin{minipage}{0.47\textwidth}
-    \begin{algorithm}[H]
-        \caption{Method with preconditioning}
-        \label{alg:precondgen}
-
-        \begin{algorithmic}
-                \Require{learning rate $\eta$, target function $f$}
-
-                \While {$w$ not converged}
-                \State $t = t+1$
-                \State $g_t \gets$ stochastic gradient
-                \State $D_t \gets$ preconditioning matrix
-                \State $w_t \gets w_{t-1} - \eta \cdot D_t^{-1} g_t$
-                \EndWhile
-        \end{algorithmic}
-    \end{algorithm}
-\end{minipage}
-\hfill
-\begin{minipage}{0.47\textwidth}
-    \begin{algorithm}[H]
-        \caption{First-ordered algorithm}
-        \label{alg:first}
-        \begin{algorithmic}
-                \Require{learning rate $\eta$, target function $f$}
-
-                \While {$w$ not converged}
-                \State $t = t+1$
-                \State $g_t \gets$ stochastic gradient
-                \State $w_t \gets w_{t-1} - \eta \cdot g_t$
-                \EndWhile
-        \end{algorithmic}
-    \end{algorithm}
-\end{minipage}
-
-We do not prescribe the exact method for obtaining $g_t$.
-In large-scale problems, stochastic gradient descent is a more efficient approach since computing the full gradient is prohibitively expensive.
-While computing the Hessian is considerably more costly, so there exist various techniques for computing the preconditioning matrix $D_t$, and we delegate the specific choice of the preconditioning approach to the authors of individual methods.
-
-\subsection{Three ways of regularizer consideration}
-
 \fi
 
+\section{Notation}
 In preconditioned methods, there exist several techniques for incorporating regularization into the optimization process.
@@
 
-\begin{theorem}
-    Suppose the Assumption \hyperref[ass:convex]{1}, \hyperref[ass:Lsmoothness]{2}, \hyperref[ass:plcondition]{3} hold, let $\varepsilon > 0$ and let the step-size satisfy
-    \begin{equation*}
-        \eta \leq \frac{2 \alpha}{\tilde{L}}
-    \end{equation*}
-    Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem \eqref{eq:general} can be bounded by
-    \begin{equation*}
-        T =  \mathcal{O}\left( \frac{\ln \frac{\Delta_0}{\epsilon}}{2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha})} \right)
-    \end{equation*}
-    \label{theor:2}
-\end{theorem}
-
-\subsection{Convergence trajectory of preconditioning methods}
-
- In the previous subsection we have proved convergence of preconditioned methods, however we have pointed out above that methods with weight decay does not converge to the initial optimized function $F = f + r$, but rather to a new function $\tilde{F} = f + \tilde{r}$.
-
-We will consider two algorithms OASIS and Adam, and its variations. Their main difference is in the calculation of the pseudo hessian.
-In Adam, the Hessian is a diagonal matrix consisting of squares of derivatives, in OASIS we have a stochastic Hessian, which is calculated through a random variable from the Randemacher distribution.
-
-We framed three methods of regularization for Adam and OASIS in \hyperref[alg:genAdam]{Algorithm 2} and \hyperref[alg:OASIS]{Algorithm 3} respectively.
-Results of our computational experiments are framed in \hyperref[fig:adams_error]{Figure 1} and \hyperref[fig:oasis_error]{Figure 2}.
-In can be seen that methods with weight decay converges only by special criterion $\nabla f + D_t \nabla r$.
-
-\begin{algorithm}[h]
-
-            \caption{Adam}\label{alg:genAdam}
-
-            \begin{algorithmic}
-            \small{
-            \Require{$\eta, \beta_1, \beta_2, \epsilon, f, r$}
-            %\State $m_0 = 0$ -- 1-st moment vector
-            %\State$v_0 = 0$ -- 2-nd moment vector
-            \While {$\theta$ not converged}
-            \State $t = t+1$
-            \State $g_t = \nabla f(w_{t-1}) + $ \textcolor{blue}{$\nabla r(w_{t-1})$}\hfill \textcolor{blue}{AdamL2}
-            \State $m_t = \beta_1 \cdot m_{t-1} + (1 - \beta_1) \cdot g_t$
-            \State $v_t = \beta_2 \cdot v_{t-1} + (1 - \beta_2) \cdot g_t^2$
-            \State $\hat{m_t} = \frac{m_t}{1-\beta_1^t} +$ \textcolor{orange}{$\nabla r(w_{t-1})$} \hfill \textcolor{orange}{AdamWH}
-            \State $\hat{v_t} = \frac{v_t}{1-\beta_2^t}$ 
-            \State $w_t = w_{t-1} - \eta \cdot \frac{\hat{m_t}}{\sqrt{v_t} + \epsilon} - $ \textcolor{red}{$\eta \nabla r(w_{t-1})$ } \hfill \textcolor{red}{AdamW}
-            \EndWhile
-            }
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[h]
-\caption{OASIS}\label{alg:OASIS}
-\begin{algorithmic}
-    \Require{$w_0, \eta_0, D_0, \theta_0 = + \infty$}    
-    \State $w_1 = w_0 - \eta \hat{D_0}^{-1} \nabla f(w_0)$
-
-    \For{$k = 1, 2, ...$}
-    \State $g_k = \nabla f(w_k) +$ \textcolor{blue}{$\nabla r(w_{t-1})$}\hfill \textcolor{blue}{OASISL2} 
-    \State $D_k = \beta D_{k-1} + (1-\beta_2) \cdot diag\left( z_k \odot \nabla^2 \left(f(w_k) + \textcolor{orange}{r(w_k)} \right) z_k \right)$ \hfill \textcolor{orange}{OASISWH}
-    \State $(\hat{D_k})_{ii} = max \{|D_k|_{i, i} ; \alpha \}$, $\forall i = \overline{1, d}$
-    \State $\eta_k = min \{ \sqrt{1 + \theta_{k-1}} \cdot \eta_{k-1}; \frac{||w_k - w_{k-1}||_{\hat{D_k}}}{2 ||\nabla f(w_k) - \nabla f(w_{k-1}) ||_{\hat{D_k}}^* } \}$
-    \State $w_{k+1} = w_k - \eta_k g_k D_k^{-1}- $ \textcolor{red}{$\eta \nabla r(w_{t-1})$ } \hfill \textcolor{red}{OASISW} 
-    \State $\theta_k = \frac{\eta_k}{\eta_{k-1}}$
-    \EndFor
-
-\end{algorithmic}
-\end{algorithm}
-
-Thus, method converges to another solution,
-
-\begin{minipage}{0.5\textwidth}
-\begin{figure}[H]
-\centering
-    \includegraphics[width=\textwidth]{pictures/mushrooms/adams_error.png}
-    \caption{Adam on dataset mushrooms}
-        \label{fig:adams_error}
-\end{figure}
-\end{minipage}
-\hfill
-\begin{minipage}{0.5\textwidth}
-\begin{figure}[H]
-\centering
-    \includegraphics[width=\textwidth]{pictures/mushrooms/oasis_error.png}
-    \caption{OASIS on dataset mushrooms}
-        \label{fig:oasis_error}
-\end{figure}
-\label{fig:error}
-\end{minipage}
-
-\begin{figure}[H]
-\centering
-    \includegraphics[width=0.9\textwidth]{pictures/mushrooms/main_adam.png}
-    \caption{Dataset: mushrooms}
-
-        \label{fig:main_mushrooms_adam}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-    \includegraphics[width=0.9\textwidth]{pictures/mushrooms/main_mushrooms.png}
-    \caption{Dataset: mushrooms}
-
-        \label{fig:main_mushrooms}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-    \includegraphics[width=0.9\textwidth]{pictures/wine/main_wine.png}
-    \caption{Dataset: wine}
-
-        \label{fig:main_wine}
-\end{figure}
-
-\subsection{Computational experiment}
-
-\bibliographystyle{unsrtnat}
-\bibliography{refs}
-
-\newpage
-\section{Appendix}
-\begin{theorem}
-Suppose the Assumption \hyperref[ass:convex]{1}, \hyperref[ass:Lsmoothness]{2} and let $\varepsilon > 0$ and let the step-size satisfy
-\begin{equation*}
-    \eta < \frac{2 \alpha}{L + l \cdot \alpha} 
-\end{equation*}
-Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem \eqref{eq:general} can be bounded by
-\begin{equation*}
-      T = \mathcal{O}\left( \frac{2\Delta_0 \Gamma \alpha } {(2\alpha - \tilde{L}\eta) \eta \varepsilon} \right)
-\end{equation*}
-
-\end{theorem}
 \begin{proof}
-
 Let's write \ref{ass:convex} for step t and $t+1$:
@@
 \begin{theorem}
-    Suppose the Assumption \hyperref[ass:convex]{1}, \hyperref[ass:Lsmoothness]{2}, \hyperref[ass:plcondition]{3} and let $\varepsilon > 0$ and let the step-size satisfy
+    Suppose the Assumption \hyperref[ass:convex]{1}, \hyperref[ass:Lsmoothness]{2}, \hyperref[ass:plcondition]{3} hold, let $\varepsilon > 0$ and let the step-size satisfy
     \begin{equation*}
@@
     \end{equation*}
+    \label{theor:2}
 \end{theorem}
-
 \begin{proof}
@@
 
-\subsection{Experiments:}
+\subsection{Convergence trajectory of preconditioning methods}
+
+ In the previous subsection we have proved convergence of preconditioned methods, however we have pointed out above that methods with weight decay does not converge to the initial optimized function $F = f + r$, but rather to a new function $\tilde{F} = f + \tilde{r}$.
+
+We will consider two algorithms OASIS and Adam, and its variations. Their main difference is in the calculation of the pseudo hessian.
+In Adam, the Hessian is a diagonal matrix consisting of squares of derivatives, in OASIS we have a stochastic Hessian, which is calculated through a random variable from the Randemacher distribution.
+
+We framed three methods of regularization for Adam and OASIS in \hyperref[alg:genAdam]{Algorithm 2} and \hyperref[alg:OASIS]{Algorithm 3} respectively.
+Results of our computational experiments are framed in \hyperref[fig:adams_error]{Figure 1} and \hyperref[fig:oasis_error]{Figure 2}.
+In can be seen that methods with weight decay converges only by special criterion $\nabla f + D_t \nabla r$.
+
+\begin{algorithm}[H]
+\caption{OASIS}\label{alg:OASIS}
+\begin{algorithmic}
+    \Require{$w_0, \eta_0, D_0, \theta_0 = + \infty$}    
+    \State $w_1 = w_0 - \eta \hat{D_0}^{-1} \nabla f(w_0)$
+
+    \For{$k = 1, 2, ...$}
+    \State $g_k = \nabla f(w_k) +$ \textcolor{blue}{$\nabla r(w_{t-1})$}\hfill \textcolor{blue}{OASISL2} 
+    \State $D_k = \beta D_{k-1} + (1-\beta_2) \cdot diag\left( z_k \odot \nabla^2 \left(f(w_k) + \textcolor{orange}{r(w_k)} \right) z_k \right)$ \hfill \textcolor{orange}{OASISWH}
+    \State $(\hat{D_k})_{ii} = max \{|D_k|_{i, i} ; \alpha \}$, $\forall i = \overline{1, d}$
+    \State $\eta_k = min \{ \sqrt{1 + \theta_{k-1}} \cdot \eta_{k-1}; \frac{||w_k - w_{k-1}||_{\hat{D_k}}}{2 ||\nabla f(w_k) - \nabla f(w_{k-1}) ||_{\hat{D_k}}^* } \}$
+    \State $w_{k+1} = w_k - \eta_k g_k D_k^{-1}- $ \textcolor{red}{$\eta \nabla r(w_{t-1})$ } \hfill \textcolor{red}{OASISW} 
+    \State $\theta_k = \frac{\eta_k}{\eta_{k-1}}$
+    \EndFor
+
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[H]
+            \caption{Adam}\label{alg:genAdam}    
+            \begin{algorithmic}
+            \small{
+            \Require{$\eta, \beta_1, \beta_2, \epsilon, f, r$}
+            %\State $m_0 = 0$ -- 1-st moment vector
+            %\State$v_0 = 0$ -- 2-nd moment vector
+            \While {$\theta$ not converged}
+            \State $t = t+1$
+            \State $g_t = \nabla f(w_{t-1}) + $ \textcolor{blue}{$\nabla r(w_{t-1})$}\hfill \textcolor{blue}{AdamL2}
+            \State $m_t = \beta_1 \cdot m_{t-1} + (1 - \beta_1) \cdot g_t$
+            \State $v_t = \beta_2 \cdot v_{t-1} + (1 - \beta_2) \cdot g_t^2$
+            \State $\hat{m_t} = \frac{m_t}{1-\beta_1^t} +$ \textcolor{orange}{$\nabla r(w_{t-1})$} \hfill \textcolor{orange}{AdamWH}
+            \State $\hat{v_t} = \frac{v_t}{1-\beta_2^t}$ 
+            \State $w_t = w_{t-1} - \eta \cdot \frac{\hat{m_t}}{\sqrt{v_t} + \epsilon} - $ \textcolor{red}{$\eta \nabla r(w_{t-1})$ } \hfill \textcolor{red}{AdamW}
+            \EndWhile
+            }
+\end{algorithmic}
+\end{algorithm}
+
+\subsection{Experiments}
+We set up experiments on the dataset \href{https://archive.ics.uci.edu/ml/datasets/mushroom}{mushrooms}, logistic regression was chosen as the model, the optimizers were AdamL2, AdamW, AdamWH, OASISL2, OASISW, OASISWH, SGD.
+Various learning rates and weight decays were considered.
+
+We observe the effect that by the new criterion the AdamW, AdamWH, OASISW, OASISWH methods converge much better than by the old one, and they also converge better than AdamL2, OASISL2.
+\begin{figure}[H]
+\begin{minipage}[h]{0.4\linewidth}
+\centering 
+\includegraphics[width=\textwidth]{pictures/mushrooms/adams_error.png}
+\caption{Adam on dataset mushrooms}
+    \label{fig:adams_error}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.4\linewidth}
+\includegraphics[width=\textwidth]{pictures/mushrooms/oasis_error.png}
+    \caption{OASIS on dataset mushrooms}
+        \label{fig:oasis_error}
+\end{minipage}
+\label{fig:oasis_error}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+    \includegraphics[width=0.7\textwidth]{pictures/mushrooms/main_adam.png}
+    \caption{Adam algrorithms on dataset: mushrooms}
+    \label{fig:main_mushrooms_adam}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+    \includegraphics[width=0.7\textwidth]{pictures/mushrooms/main_mushrooms.png}
+    \caption{Compare different optimization algorithms on dataset: mushrooms}
+    \label{fig:main_mushrooms}
+\end{figure}
+As we can see, the AdamW method shows the best result compared to other optimization algorithms, it is also clear that the new AdamW criterion converges much faster than the old one, and thus it has a better generalization ability compared to other methods.
+
+\begin{figure}[H]
+\centering
+    \includegraphics[width=0.7\textwidth]{pictures/wine/main_wine.png}
+    \caption{Compare different optimization algorithms on dataset: mushrooms}
+
+        \label{fig:main_wine}
+\end{figure}
+Here we see a similar picture as in the last example.
 \subsubsection{Mushrooms}
+Here are all the experiments that were performed on the mushrooms dataset.
+Learning rate and weight decay are signed for each method on the picture, as well as the criterion used to calculate the error.
 \begin{figure}[h]
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
 \begin{minipage}[h]{0.5\linewidth}
@@
 \subsubsection{Wine}
-
+Here are all the experiments that were performed on the \href{https://archive.ics.uci.edu/ml/datasets/wine}{wine} dataset.
+Learning rate and weight decay are signed for each method on the picture, as well as the criterion used to calculate the error.
 \begin{figure}[H]
@@
 
+And to finalize our results let's show the results of training \href{https://pytorch.org/vision/main/models/generated/torchvision.models.resnet18.html}{ResNet18} on 4 different optimizators with \href{https://pytorch.org/docs/stable/generated/torch.optim.lr_scheduler.CosineAnnealingLR.html}{CosineAnnealingLr} on dataset \href{https://www.cs.toronto.edu/~kriz/cifar.html}{CIFAR10}.
+
+\begin{figure}[H]
+\centering
+    \includegraphics[width=0.7\textwidth]{pictures/nn_results.png}
+    \caption{Compare different optimization algorithms on dataset: CIFAR10}
+
+        \label{fig:main_resnet18}
+\end{figure}
+AdamW shows the worst results for the loss function, but wins all other methods in accuracy on the test sample, exactly this generalizing ability of the AdamW method was mentioned earlier.
+
+\subsection{Conclusion:}
+This paper investigated preconditioning methods with weight decay regularization.
+Two theorems were established for these methods, each under different assumptions regarding the target loss function.
+The theorems demonstrated that these methods converge to a different criterion that is significantly superior to the original one.
+Consequently, these methods exhibit reduced overfitting and greater generalization ability, leading to excellent performance when training neural networks.
+Empirical results were also presented to support these findings.
+
+\bibliographystyle{unsrtnat}
+\bibliography{refs}
+
 \end{document}

### 2023-05-02 code/adamwh.py

@@ -220,28 +220,9 @@ def _single_tensor_myadamw(params: List[Tensor],
             
             
             ### PROBABILITY ALGORITHM!!! ###
-            vera = torch.randint(0, 3, (1,))
-            if int(vera) == 0:
-                # под гессиан
-                ### OUR CHANGING!!!
-                tmp = exp_avg + weight_decay * param
-                param.addcdiv_(tmp, denom, value=-step_size)
-                ###
-            elif int(vera) == 1:
-                # и туда и сюда
-                ### OUR CHANGING!!!
-                param.mul_(1 - lr * weight_decay)
-                tmp = exp_avg + weight_decay * param
-                param.addcdiv_(tmp, denom, value=-step_size)
-                ###
-            elif int(vera) == 2:
-                # только снаружи
-                ### OUR CHANGING!!!
-                param.mul_(1 - lr * weight_decay)
-                param.addcdiv_(exp_avg, denom, value=-step_size)
-                ###
-            elif int(vera) == 3:
-                param.addcdiv_(exp_avg, denom, value=-step_size)
+            param.mul_(1 - lr * weight_decay)
+            param.addcdiv_(exp_avg, denom, value=-step_size)
+
 
             
 
@@ -360,29 +341,7 @@ def _multi_tensor_myadamw(params: List[Tensor],
         ###
         '''
 
-        ### PROBABILITY ALGORITHM!!! ###
-        vera = torch.randint(0, 3, (1,))
-        if int(vera) == 0:
-            # под гессиан
-            ### OUR CHANGING!!!
-            wd = torch._foreach_mul(params, weight_decay)
-            new_exp_avgs = torch._foreach_add(exp_avgs, wd)
-            torch._foreach_addcdiv_(params, new_exp_avgs, denom, step_size)
-            ###
-        elif int(vera) == 1:
-            # и туда и сюда
-            ### OUR CHANGING!!!
-            torch._foreach_mul_(params, 1 - lr * weight_decay)
-            wd = torch._foreach_mul(params, weight_decay)
-            new_exp_avgs = torch._foreach_add(exp_avgs, wd)
-            torch._foreach_addcdiv_(params, new_exp_avgs, denom, step_size)
-            ###
-        elif int(vera) == 2:
-            # только снаружи
-            ### OUR CHANGING!!!
-            torch._foreach_mul_(params, 1 - lr * weight_decay)
[…]

### 2023-05-02 code/main.py

@@ -12,7 +12,7 @@ import os
 import argparse
 import sys
 
-from myadam import MyAdamW
+from adamwh import MyAdamW
 
 from resnet import ResNet18
 
@@ -20,13 +20,11 @@ from tqdm import tqdm
 #from torch.utils import progress_bar
 from torch.utils.tensorboard import SummaryWriter
 
-
 def test(epoch):
     global best_acc
     global test_step
     net.eval()
     test_loss = 0
-    test_loss_true = 0
     correct = 0
     total = 0
     with torch.no_grad():
@@ -38,15 +36,11 @@ def test(epoch):
             loss = criterion(outputs, targets)
 
             test_loss += loss.item()
-            #
-            test_loss_true += loss.item()
-
             _, predicted = outputs.max(1)
             total += targets.size(0)
             correct += predicted.eq(targets).sum().item()
             
             writer.add_scalar('Testing loss', test_loss/(batch_idx+1),global_step=test_step)
-            writer.add_scalar('Testing loss true', test_loss_true/(batch_idx+1),global_step=test_step)
             writer.add_scalar('Testing accuracy', 100.*correct/total, global_step=test_step)
             
             loop.set_description(f"{full_name}Epoch (Test)[{epoch}/{num_epoch}]")
@@ -65,7 +59,7 @@ def test(epoch):
             os.mkdir('checkpoint')
         torch.save(state, f'./checkpoint/ckpt.pth')
         best_acc = acc
-    return test_loss, correct, total, test_loss_true
+    return test_loss, correct, total
 
 # Training
 def train(epoch):
@@ -73,7 +67,6 @@ def train(epoch):
     global train_step
     net.train()
     train_loss = 0
-    train_loss_true = 0
     correct = 0
     total = 0
     loop = tqdm(enumerate(trainloader), total=len(trainloader), leave=False)
@@ -88,23 +81,17 @@ def train(epoch):
         train_step += 1
 
         train_loss += loss.item()
-        #true loss
-        train_loss_true += loss.item() + 
-        
         _, predicted = outputs.max(1)
         total += targets.size(0)
         correct += predicted.eq(targets).sum().item()
         
         writer.add_scalar('Training loss', train_loss/(batch_idx+1),global_step=train_step)
-        writer.add_scalar('Training loss true', train_loss_true/(batch_idx+1),global_step=test_step)
         writer.add_scalar('Training accuracy', 100.*correct/total, global_step=train_step)
-        
 
[…]
